% ============================================================
% CLASS CARD POOLS — VOLUME 1 (FULL SIZE)
% Zealot, Circuit Rider, Arcanist, Dynast — 13 archetypes,
% 15 cards each. Supersedes the sample entries in
% class-card-pools.tex for these classes.
% Format: Name — Momentum cost — Level — tags — effect.
% (Dup ×N) = up to N copies permitted in a deck.
% All numbers remain tuning placeholders.
% ============================================================

\chapter{Class Card Pools, Volume 1}

\section{Zealot}

\subsection{The Line-Holder}
\begin{itemize}
    \item \textbf{Shield Up} --- 1 --- L1 --- (Dup ×3) --- +1 Defend until your side's next surge.
    \item \textbf{Hold Here} --- 1 --- L1 --- Stance --- While you don't move, allies within 2 tiles gain +1 Defend and can't be forced to move.
    \item \textbf{You Face Me} --- 1 --- L1 --- One enemy within 3 tiles must include you in its next attack or lose 1 die from it.
    \item \textbf{Stand Fast} --- 1 --- L1 --- Reaction --- Negate forced movement or knockdown on you or an adjacent ally.
    \item \textbf{Guarded Advance} --- 1 --- L1 --- Move 1 tile; +1 Defend this round.
    \item \textbf{Not One Step} --- 1 --- L2 --- Stance --- Enemies leaving your reach take a free Strike from you at +1 die.
    \item \textbf{Brace the Wall} --- 1 --- L2 --- Stance --- Allies adjacent to you can't be pushed or knocked down.
    \item \textbf{Taunt the Pack} --- 1 --- L2 --- Up to 2 enemies within 3 tiles must include you in their next attacks or take --1 die.
    \item \textbf{The Door Does Not Open} --- 1 --- L3 --- Reaction --- When an enemy tries to pass within your reach, stop its movement and Strike it.
    \item \textbf{Anchor Point} --- 1 --- L3 --- This round, allies within 2 tiles may use your Defend value.
    \item \textbf{The Wall Answers} --- 1 --- L4 --- Reaction --- When an enemy damages an ally within 2 tiles, Strike it (+2 dice) if it's in reach.
    \item \textbf{Immovable} --- 1 --- L4 --- Stance --- +1 Armor while you haven't moved this round; immune to fear while any ally stands behind you.
    \item \textbf{Redoubt} --- 2 --- L5 --- One-Shot --- Until your side's next surge, attacks on allies within 2 tiles target you instead; +2 Armor.
    \item \textbf{Witnessed Stand} --- 1 --- L5 --- While you're below half HP and holding ground: +1 die on all rolls; allies who can see you clear fear.
    \item \textbf{Where I Stand, the Line} --- 2 --- L6 --- One-Shot --- For the scene, enemies cannot pass within 2 tiles of you without ending their movement; +1 Defend.
\end{itemize}

\subsection{The Intercessor}
\begin{itemize}
    \item \textbf{A Word of Grace} --- 1 --- L1 --- (Dup ×3) --- An ally within 5 tiles heals 1 HP or gains +1 die on their next save.
    \item \textbf{Spoken Plainly} --- 1 --- L1 --- Heal an ally within 5 tiles 2 HP or clear one fear/despair effect; say aloud, in character, why they will hold.
    \item \textbf{Bless the Blade} --- 1 --- L1 --- An ally's next attack counts as Heavens-aligned and gains +1 die.
    \item \textbf{Keep Watch Over Them} --- 1 --- L1 --- Stance --- Allies within 3 tiles gain +1 die on saves.
    \item \textbf{Steady Voice} --- 1 --- L1 --- Reaction --- Cancel a fear or despair effect as it lands on an ally within 5 tiles.
    \item \textbf{Borrowed Light} --- 1 --- L2 --- An ally's next roll this round gains +2 dice; +3 if they tell the table what they're afraid of.
    \item \textbf{Shared Burden} --- 1 --- L2 --- Take up to 3 damage from an ally within 3 tiles onto yourself.
    \item \textbf{Litany Against the Dark} --- 1 --- L2 --- Stance --- Undead and Shadow-aligned enemies take --1 die attacking allies within 3 tiles of you.
    \item \textbf{Confession Heard} --- 1 --- L3 --- Out of combat: an ally clears one lingering mental affliction and heals 2 HP; you carry what you heard.
    \item \textbf{Grace Under Fire} --- 1 --- L3 --- Heal 2 HP each to two allies within 5 tiles.
    \item \textbf{The Vapor Carries It} --- 1 --- L4 --- One-Shot --- Ask the GM one true question about the present danger; the answer arrives as vision.
    \item \textbf{Stand Them Up} --- 1 --- L4 --- Reaction --- An ally dropping to 0 HP drops to 1 instead and may move 1 tile.
    \item \textbf{The Honest Prayer} --- 1 --- L5 --- Your next Heavens invocation this scene gains +2 automatic successes; the price is unchanged and you know it.
    \item \textbf{Answered} --- 2 --- L6 --- One-Shot --- Choose: all allies heal 3 HP, or one Shadow-aligned enemy takes hits equal to your Religion.
    \item \textbf{The Formation Prays} --- 2 --- L7 --- One-Shot --- Every ally who speaks one honest sentence gains +1 die on all rolls until the scene ends.
\end{itemize}

\subsection{The Lamplighter}
\begin{itemize}
    \item \textbf{Lantern Strike} --- 1 --- L1 --- (Dup ×3) --- Strike; +1 die against undead and Shadow-aligned targets.
    \item \textbf{Cast Light} --- 1 --- L1 --- Illuminate 5 tiles: hidden things are revealed; light-hating things there lose 1 Defend.
    \item \textbf{Lamp Oil and Iron} --- 1 --- L1 --- Stance --- Your attacks this round ignore the Armor of undead and Shadow-aligned creatures.
    \item \textbf{Carry the Flame} --- 1 --- L1 --- An ally's weapon burns clean for a round: +1 die vs Shadow-aligned targets.
    \item \textbf{Read the Dark} --- 1 --- L1 --- Learn whether Shadow influence is present within 5 tiles, and roughly where.
    \item \textbf{No Shadow Here} --- 1 --- L2 --- Stance --- Enemies gain no benefit from darkness or concealment within 3 tiles of you.
    \item \textbf{Brand} --- 1 --- L2 --- Your Strike marks the target: it sheds light, can't hide, and takes +1 hit from Heavens-aligned attacks this scene.
    \item \textbf{Burn It Out} --- 1 --- L2 --- End one ongoing Shadow effect on an ally or a tile.
    \item \textbf{I See You} --- 1 --- L3 --- Name one visible enemy: your side's attacks against it gain +1 die until it drops. It knows.
    \item \textbf{The Searing Word} --- 1 --- L3 --- 2 hits to one undead or Shadow-aligned target within 5 tiles; it saves or recoils 1 tile.
    \item \textbf{Vigil Flame} --- 1 --- L4 --- Stance --- While you hold a light source, allies within its glow gain +1 die on saves vs Shadow and Nightmare effects.
    \item \textbf{Hunt the Source} --- 1 --- L4 --- Learn the direction and rough distance of the strongest Shadow presence within the scene or site.
    \item \textbf{Sunrise Discipline} --- 1 --- L5 --- Reaction --- When a Shadow effect targets your side, you take it alone, with +2 dice on the save.
    \item \textbf{Dawn, Early} --- 2 --- L6 --- One-Shot --- Burst of revealing light: enemies within 3 tiles take 2 hits (Shadow-aligned: 4); nothing within it remains concealed.
    \item \textbf{The Long Watch Ends} --- 2 --- L7 --- One-Shot --- Against one named Shadow entity you have witnessed for a full session: this scene, your attacks against it ignore Defend and Armor.
\end{itemize}

\section{Circuit Rider}

\subsection{The Shepherd}
\begin{itemize}
    \item \textbf{Field Dressing} --- 1 --- L1 --- (Dup ×3) --- Heal an adjacent ally 2 HP.
    \item \textbf{Seen and Tended} --- 1 --- L1 --- Heal an adjacent ally 3 HP; 4 if you've named a true thing about them this scene.
    \item \textbf{Walk the Rounds} --- 1 --- L1 --- Move your full Move; each ally you pass adjacent to heals 1 HP.
    \item \textbf{Quiet the Panic} --- 1 --- L1 --- Clear fear or despair from an ally within 3 tiles.
    \item \textbf{Comfort of the Familiar} --- 1 --- L1 --- Stance --- Allies within 3 tiles gain +1 die on morale and fear saves.
    \item \textbf{Get Up. You Held.} --- 1 --- L2 --- Reaction --- An ally dropping to 0 HP drops to 1 instead.
    \item \textbf{Tend the Flock} --- 1 --- L2 --- Heal 1 HP to every ally within 3 tiles.
    \item \textbf{The Remembered Hurt} --- 1 --- L2 --- Clear one poison, disease, or lingering injury from an adjacent ally.
    \item \textbf{Circuit Kit} --- 1 --- L3 --- Consumable ×3 --- Bearers may spend to heal 2 HP or reroll a save.
    \item \textbf{Sit With the Dying} --- 1 --- L3 --- An ally at 0 HP stabilizes automatically and wakes with 2 HP at scene's end.
    \item \textbf{Shepherd's Eye} --- 1 --- L4 --- Learn the true condition of everyone in sight: HP ranges, afflictions, who is lying about being fine.
    \item \textbf{Carry Their Weight} --- 1 --- L4 --- Reaction --- Transfer one condition or affliction from an ally within 3 tiles to yourself, at --1 severity.
    \item \textbf{The Flock Stands} --- 1 --- L5 --- All allies within 5 tiles heal 2 HP and clear one condition each.
    \item \textbf{No One Dies Tonight} --- 2 --- L6 --- One-Shot --- Until end of scene, allies within 5 tiles can't be reduced below 1 HP by the first source that would do it each round.
    \item \textbf{Twenty Years on This Road} --- 2 --- L7 --- One-Shot --- Out of combat: fully heal one person, body and mind --- the great restoration of the circuit; the community will talk about it for a generation.
\end{itemize}

\subsection{The Witness}
\begin{itemize}
    \item \textbf{Look Again} --- 1 --- L1 --- (Dup ×3) --- Reroll a Perceive or Investigate roll with +1 die.
    \item \textbf{What Changed Here} --- 1 --- L1 --- Ask the GM: what in this scene differs from how it should be? True answer.
    \item \textbf{Hold Their Gaze} --- 1 --- L1 --- One creature must engage with you or visibly, unmistakably avoid you; either tells you something.
    \item \textbf{Mark the Face} --- 1 --- L1 --- Perfectly memorize a person, mark, or document; recognize it ever after, through disguise or forgery.
    \item \textbf{The Rider's Question} --- 1 --- L1 --- +2 dice on one Convince or Investigate roll made gently.
    \item \textbf{Say It Plain} --- 1 --- L2 --- One creature must answer your next question truthfully or visibly refuse.
    \item \textbf{Seen Through} --- 1 --- L2 --- Reaction --- When someone lies in your presence, know it; gain +1 die against them this scene.
    \item \textbf{Nothing Hides From Attention} --- 1 --- L2 --- One hidden, invisible, or disguised creature within 5 tiles is revealed to you.
    \item \textbf{The Account Is Kept} --- 1 --- L3 --- Stance --- Enemies within 5 tiles gain nothing from concealment, disguise, or lies while you watch.
    \item \textbf{Testimony} --- 1 --- L3 --- Recount what you witnessed: allies gain +1 die against a threat you've described, this scene.
    \item \textbf{The Weight of Being Seen} --- 1 --- L4 --- One enemy that knows you've witnessed its acts takes --1 die on all rolls against your side this scene.
    \item \textbf{Read the Room Entire} --- 1 --- L4 --- Learn every present creature's disposition, allegiance, and immediate intent.
    \item \textbf{Enter It in the Book} --- 2 --- L5 --- One-Shot --- Name an enemy: for the scene your side knows its position and it can surprise no one.
    \item \textbf{The Unblinking Hour} --- 1 --- L5 --- Stance --- You cannot be deceived, misdirected, or surprised; illusions simply fail against you.
    \item \textbf{I Was There} --- 2 --- L7 --- One-Shot --- Your witness becomes legally, socially, spiritually decisive: one disputed fact you personally observed is settled, everywhere it matters.
\end{itemize}

\subsection{The Long Rider}
\begin{itemize}
    \item \textbf{Press On} --- 1 --- L1 --- (Dup ×3) --- Move your full Move as a second move this surge.
    \item \textbf{Road Legs} --- 1 --- L1 --- Stance --- You and adjacent allies gain +1 Move; difficult ground doesn't slow you.
    \item \textbf{Know the Fords} --- 1 --- L1 --- Automatically find the crossing, gate, or path through one terrain obstacle.
    \item \textbf{Saddle-Born} --- 1 --- L1 --- Mount or dismount free; your mount uses your dice for saves.
    \item \textbf{Traveler's Eye} --- 1 --- L1 --- Assess a route or settlement at a glance: dangers, resources, mood.
    \item \textbf{I Know a Way} --- 1 --- L2 --- Move an ally within 5 tiles up to their Move.
    \item \textbf{Ride Through} --- 1 --- L2 --- Move your full Move ignoring enemies' reach; +1 Defend during it.
    \item \textbf{The Circuit's Pace} --- 1 --- L2 --- Stance --- Your party travels one step faster overland; you never count as lost.
    \item \textbf{Courier's Burst} --- 1 --- L3 --- An ally acts immediately after you at --1 Momentum cost (min 0 for a Move).
    \item \textbf{The Lantern at Dusk} --- 1 --- L4 --- Until end of scene, allies ending their move adjacent to you heal 1 HP and clear fatigue.
    \item \textbf{Weather Sense} --- 1 --- L3 --- Know the next day's weather and one hazard on the road ahead.
    \item \textbf{Shortcut} --- 1 --- L4 --- One-Shot --- Your party's next journey takes half the time; you knew a way, because you always know a way.
    \item \textbf{Everyone Mounts} --- 1 --- L5 --- Your whole side gains +2 Move this round.
    \item \textbf{Rider on the Ridge} --- 2 --- L6 --- One-Shot --- Help arrives: an NPC ally you plausibly know from your circuit enters the scene's edge, favorably disposed.
    \item \textbf{The Whole Circuit Answers} --- 2 --- L7 --- One-Shot --- Word goes down the roads: within days, the communities of your circuit send what you asked for --- hands, supplies, shelter, or forty quiet witnesses.
\end{itemize}

\section{Arcanist}

\subsection{The Ward-Wright}
\begin{itemize}
    \item \textbf{Warding Gesture} --- 1 --- L1 --- (Dup ×3) --- An ally within 3 tiles gains +1 Defend until your next surge.
    \item \textbf{Chalk Line} --- 1 --- L1 --- A 3-tile line: enemies crossing it lose 1 die from their next action.
    \item \textbf{Seal the Door} --- 1 --- L1 --- Hold one portal or passage shut (2 successes to force).
    \item \textbf{Damp the Working} --- 1 --- L1 --- Reaction --- Reduce one incoming supernatural effect's hits or successes by 1.
    \item \textbf{Anchor Glyph} --- 1 --- L1 --- One tile: allies standing there can't be moved by any force.
    \item \textbf{Warding Circle} --- 1 --- L2 --- A 1-tile circle: allies inside gain +1 Defend and +1 die on saves; lasts until you move.
    \item \textbf{Shaped Exclusion} --- 1 --- L2 --- Choose a creature type: it cannot willingly enter one tile you ward, this scene.
    \item \textbf{Grounding Rod} --- 1 --- L2 --- Stance --- Supernatural effects targeting allies within 2 tiles of you lose 1 die.
    \item \textbf{Extend the Line} --- 1 --- L3 --- Lengthen or reposition one of your active wards; it gains +1 to its effect.
    \item \textbf{Containment} --- 2 --- L4 --- Box one enemy in force (Defend 2, HP 4 walls) for a round.
    \item \textbf{Layered Wards} --- 1 --- L4 --- Stance --- You may maintain two ward effects simultaneously.
    \item \textbf{The Quiet Hall} --- 1 --- L5 --- A 3-tile zone: sound, panic, and fear behave conservatively --- no fear effects, no surprise, inside it.
    \item \textbf{Ward Against the Named} --- 1 --- L5 --- Name an enemy: your wards count double against it specifically.
    \item \textbf{The Vellhame Protocol} --- 2 --- L6 --- One-Shot --- Suppress all supernatural effects in a 3-tile radius for one round --- including your side's.
    \item \textbf{The Standing Ward} --- 2 --- L7 --- One-Shot --- Ward a site (a building, a camp, a bridge) for a full day: hostile supernatural forces cannot cross, and you know if anything tries.
\end{itemize}

\subsection{The Open Channel}
\begin{itemize}
    \item \textbf{Spark} --- 1 --- L1 --- (Dup ×3) --- 2 hits to one target within 5 tiles.
    \item \textbf{Arc} --- 1 --- L1 --- 3 hits to one target within 5 tiles; you may take 1 damage to make it 4.
    \item \textbf{Flare} --- 1 --- L1 --- 1 hit to up to 3 targets within 3 tiles.
    \item \textbf{Vent} --- 1 --- L1 --- Reaction --- When damaged, release: the attacker (if within 3 tiles) takes 1 hit.
    \item \textbf{Hold the Charge} --- 1 --- L1 --- Your next Channel card this scene gains +1 hit.
    \item \textbf{Discharge} --- 1 --- L2 --- 2 hits to every enemy in a 2-tile cone; take 1 damage per extra tile of reach you add.
    \item \textbf{Lash} --- 1 --- L2 --- 2 hits to a target within 5 tiles and pull it 2 tiles toward you or push it 2 away.
    \item \textbf{Burn Bright} --- 1 --- L2 --- Take 1 damage: your next attack this surge gains +2 dice or +1 hit.
    \item \textbf{Sustained Beam} --- 1 --- L3 --- 2 hits to one target now and 2 more on your next surge if you don't move.
    \item \textbf{Overdraw} --- 1 --- L4 --- Stance --- Your Channel cards deal +1 hit; you take 1 damage at the start of each of your surges while this holds.
    \item \textbf{Shatterpoint} --- 1 --- L4 --- 3 hits to one target; on any hit, its Armor drops by 1 this scene.
    \item \textbf{The Mass Speaks} --- 1 --- L5 --- Add automatic hits equal to half your level (round down) to one Channel attack; the GM notes the ease.
    \item \textbf{Rolling Thunder} --- 2 --- L5 --- 2 hits to every enemy in a 3-tile line; the ground smokes.
    \item \textbf{The Cascade, Glimpsed} --- 2 --- L7 --- One-Shot --- 6 hits, 3-tile radius, centered on you; allies included unless warded.
    \item \textbf{Carried Well} --- 1 --- L6 --- One-Shot --- Cancel all self-damage you would take from Channel cards this scene: tonight, the stewardship holds.
\end{itemize}

\subsection{The Book-Bound}
\begin{itemize}
    \item \textbf{Consult the Names} --- 1 --- L1 --- (Dup ×2) --- Look at the top 3 cards of your holstered pile; load one (discard from hand if over 5).
    \item \textbf{Marginalia} --- 1 --- L1 --- +2 dice on one Study roll; the book has notes.
    \item \textbf{A Familiar Passage} --- 1 --- L1 --- Reroll any roll that duplicates one you've made this scene, at +1 die.
    \item \textbf{Chained and Carried} --- 1 --- L1 --- Stance --- Your book can't be taken from you; attempts fail and you know who tried.
    \item \textbf{Bookmark} --- 1 --- L1 --- Set aside the top card of your holstered pile face-down; load it later as a free action.
    \item \textbf{A Dead Master's Trick} --- 1 --- L2 --- Copy the printed effect of any card in your expended pile, at +1 cost.
    \item \textbf{Cross-Reference} --- 1 --- L2 --- Shuffle your expended pile into holstered now.
    \item \textbf{The Index Knows} --- 1 --- L2 --- Name a card in your deck: put it on top of your holstered pile.
    \item \textbf{The Book Remembers} --- 1 --- L3 --- Reaction --- When an enemy uses a supernatural ability, learn what it is and one weakness.
    \item \textbf{Borrowed Hand} --- 1 --- L3 --- Play a card from an adjacent willing ally's expended pile as if yours, at +1 cost.
    \item \textbf{Errata} --- 1 --- L4 --- Reaction --- When a card of yours fully fails, return it to your hand instead of expending it.
    \item \textbf{The Weather Turns} --- 1 --- L4 --- Stance --- Once per surge, your first card costs 1 less Momentum (min 1); the book is in a mood to help.
    \item \textbf{Read Ahead} --- 1 --- L5 --- Look at the top 5 of holstered; reorder them.
    \item \textbf{Forty Hands on the Pen} --- 2 --- L6 --- One-Shot --- Play up to 3 cards from your expended pile this surge, paying costs; the book is briefly awake.
    \item \textbf{Add Your Name} --- 2 --- L7 --- One-Shot --- Commune with the housed dead: ask three questions any former holder of your book could answer. They answer. They are glad of the company.
\end{itemize}

\section{Dynast}

\subsection{The Thirsting Line}
\begin{itemize}
    \item \textbf{Flicker Step} --- 1 --- L1 --- (Dup ×3) --- Move 2 tiles ignoring reach and terrain.
    \item \textbf{Arrival Without Transit} --- 1 --- L1 --- Move full Move and Strike; +2 dice if the target hadn't seen you this round.
    \item \textbf{The Taste} --- 1 --- L1 --- After damaging a living creature in melee: heal 2 HP and learn one true physical fact about it.
    \item \textbf{Pale Grace} --- 1 --- L1 --- Stance --- +1 Defend; climbing and balance cost nothing.
    \item \textbf{Cold Poise} --- 1 --- L1 --- Reaction --- +2 Defend against one attack you can see coming.
    \item \textbf{Night's Own} --- 1 --- L2 --- Stance --- In dim light or darkness: +1 Move, +1 Defend, perfect sight.
    \item \textbf{Twin Cuts} --- 1 --- L2 --- Strike twice at --1 die each.
    \item \textbf{The Old Courtesy} --- 1 --- L2 --- +2 dice on one social roll; House manners open what force can't.
    \item \textbf{Drink Deep} --- 1 --- L3 --- Against a grappled, willing, or helpless target: heal 4 HP; the target loses 1 die next action.
    \item \textbf{Read the Vintage} --- 1 --- L3 --- Taste blood (consenting or spilled): learn ancestry, health, poison, expression --- the full Corvara diagnostic.
    \item \textbf{Blur of Intent} --- 1 --- L4 --- Reaction --- An attack that would hit you misses: you were already elsewhere within 1 tile.
    \item \textbf{Hunter of the Restless Dead} --- 1 --- L4 --- Stance --- +2 dice on attacks and Perceive against undead; they read you as a rival, not prey.
    \item \textbf{The Tithe Honored} --- 1 --- L5 --- A willing ally gives freely: they take 2 damage; you heal 4 and gain +1 die on all rolls this round. Recorded, compensated, remembered.
    \item \textbf{The Red Ledger} --- 2 --- L6 --- One-Shot --- Against a creature you have tasted: this Strike ignores Defend, and you know its location for the session.
    \item \textbf{Faster Than Doubt} --- 2 --- L7 --- One-Shot --- This surge, take 3 actions for 1 Momentum total, all movement free between them. Watching it is not comfortable.
\end{itemize}

\subsection{The Grown Line}
\begin{itemize}
    \item \textbf{Plated Blow} --- 1 --- L1 --- (Dup ×3) --- Strike with grown bone: +1 die.
    \item \textbf{Blade-Ridge} --- 1 --- L1 --- Stance --- Your unarmed Strikes use grown edges: +1 die and lethal.
    \item \textbf{Shrug It Off} --- 1 --- L1 --- Reaction --- Reduce one attack's hits on you by 1.
    \item \textbf{Broad as a Gate} --- 1 --- L1 --- Stance --- Enemies can't move through your tile or the tiles adjacent to it on your flanks.
    \item \textbf{Heavy Presence} --- 1 --- L1 --- +2 dice on one Intimidate roll; your silhouette does most of it.
    \item \textbf{Answer in Bone} --- 1 --- L2 --- Reaction --- When an attack damages you, +1 Armor until end of scene (max +3).
    \item \textbf{Horn and Weight} --- 1 --- L2 --- Move in a line and Strike; on a hit, push 2 tiles and knock down.
    \item \textbf{Grip of the Line} --- 1 --- L2 --- Grapple at +2 dice; a held foe can't speak incantations or signal.
    \item \textbf{Living Bulwark} --- 1 --- L3 --- Stance --- Allies directly behind you can't be targeted by Shoot attacks.
    \item \textbf{Crash Through} --- 1 --- L3 --- Move through a wall, door, or barricade of ordinary make, destroying it.
    \item \textbf{The Plate Reads True} --- 1 --- L4 --- Show your history: +2 dice on one social roll with anyone who respects scars, service, or the Gap.
    \item \textbf{Grown for the Blow} --- 1 --- L4 --- Reaction --- An attack that would deal 3+ hits to you deals 1 instead; your plate cracks loudly and re-knits.
    \item \textbf{Elder's Reach} --- 1 --- L5 --- Your Strikes reach 2 tiles this scene; the ridges have grown long.
    \item \textbf{The Seat, Refused} --- 2 --- L7 --- One-Shot --- Until end of scene: you cannot be moved, knocked down, or reduced below 1 HP by attacks; you also cannot move.
    \item \textbf{Eleven Generations Watching} --- 2 --- L6 --- One-Shot --- Plant yourself: allies within 3 tiles gain +1 Defend and +2 dice vs fear for the scene; you are, briefly, the keep.
\end{itemize}

\subsection{The Living Iron}
\begin{itemize}
    \item \textbf{Iron Fist} --- 1 --- L1 --- (Dup ×3) --- Strike: +1 die, and metal or construct targets take +1 hit.
    \item \textbf{Take the Charge} --- 1 --- L1 --- Absorb a vim source: bank 3 ebbs on this card's line (max 6).
    \item \textbf{Discharge Through the Hands} --- 1 --- L1 --- Spend banked ebbs: 1 hit per ebb to a touched creature, or power a device for a scene.
    \item \textbf{Weight of the Works} --- 1 --- L1 --- Stance --- You can't be pushed or knocked down; you sink in water and don't care.
    \item \textbf{Read the Alloy} --- 1 --- L1 --- Touch metal or bio-metal: learn its make, flaws, and history.
    \item \textbf{Live Wire} --- 1 --- L2 --- Stance --- Creatures grappling or striking you barehanded take 1 hit; spend 1 ebb to make it 2 this round.
    \item \textbf{Magnetize} --- 1 --- L2 --- Pull a metal object (up to a weapon) within 3 tiles to your hand, or cling to any metal surface.
    \item \textbf{Furnace Eyes} --- 1 --- L2 --- See heat and current: hidden warm bodies and live lines within 5 tiles are revealed to you.
    \item \textbf{Ringing Bones} --- 1 --- L3 --- Stance --- +1 Armor; immune to vim/electrical harm, banking 1 ebb whenever it's tried.
    \item \textbf{Arc Across} --- 1 --- L3 --- Spend 2 ebbs: 2 hits to a target within 3 tiles and 1 hit to one enemy adjacent to it.
    \item \textbf{Bar the Way} --- 1 --- L4 --- Your body is the gate: while you hold a doorway or gap, it counts as sealed (2 successes to force, and you Strike whoever tries).
    \item \textbf{Kin to the Herd} --- 2 --- L5 --- One-Shot --- A spagyric frame or chassis in sight treats you as its handler for the scene.
    \item \textbf{Overclock the Flesh} --- 1 --- L5 --- Spend 3 ebbs: gain +1 Move and +1 die on all physical rolls this round.
    \item \textbf{Cold Anvil Certainty} --- 1 --- L6 --- One-Shot --- Repair yourself or a construct/frame fully out of combat, or 5 HP in combat; hands only.
    \item \textbf{The Capacitor} --- 2 --- L7 --- One-Shot --- Bank without limit this scene, then release it all: 1 hit per ebb, divided among enemies within 3 tiles. Cold Anvil felt that.
\end{itemize}

\subsection{The Drowned Line}
\begin{itemize}
    \item \textbf{Raking Claws} --- 1 --- L1 --- (Dup ×3) --- Strike: +1 die; on a hit, the target bleeds (1 hit next round).
    \item \textbf{Acid in the Veins} --- 1 --- L1 --- Stance --- Creatures hitting you in melee take 1 hit.
    \item \textbf{Amphibious Assault} --- 1 --- L1 --- Move full Move through water (unimpeded) and Strike at +1 die.
    \item \textbf{Nictitating Calm} --- 1 --- L1 --- Reaction --- Ignore one blinding, gas, or spray effect entirely.
    \item \textbf{Read the Water} --- 1 --- L1 --- Learn everything moving in water within 10 tiles: number, size, direction.
    \item \textbf{The Drowned Court's Grip} --- 1 --- L2 --- Grapple with claws: +2 dice; a held foe takes 1 acid hit per round.
    \item \textbf{Spit} --- 1 --- L2 --- Acid at 3 tiles: 2 hits; the target's Armor drops 1 this scene.
    \item \textbf{Cold-Blood Patience} --- 1 --- L2 --- Stance --- Remain motionless: near-invisible to warmth and motion senses; +2 dice on your next attack from stillness.
    \item \textbf{Regrow} --- 1 --- L3 --- Heal 3 HP; clear one lingering injury; over downtime, regrow what was lost.
    \item \textbf{Shed the Grip} --- 1 --- L3 --- Reaction --- Escape any grapple, bond, or hold automatically; molted skin stays behind, and it's acid too.
    \item \textbf{Delta Manners} --- 1 --- L4 --- +2 dice on one negotiation over salvage, passage, or property; the Court's grammar is unanswerable.
    \item \textbf{Death Roll} --- 1 --- L4 --- Against a grappled foe: 3 hits and it's prone, disoriented (--1 die) next round.
    \item \textbf{The Molt} --- 1 --- L5 --- One-Shot --- Shed entirely: clear all conditions, heal 4 HP, and this scene's first attack against you misses --- it hit the skin.
    \item \textbf{Take It Under} --- 2 --- L6 --- One-Shot --- In or beside water: drag one enemy your size or smaller beneath; it spends its side's next 2 Momentum surfacing or begins to drown.
    \item \textbf{Blood the Water} --- 2 --- L7 --- One-Shot --- Open your own veins into the current (take 2 damage): every enemy in the water this scene takes 1 hit per round and fights at --1 die. The Greywater remembers whose it is.
\end{itemize}
