% ============================================================
% SPECIES CARD POOLS (first draft)
% ------------------------------------------------------------
% AUTHOR SPEC: 5 of the base deck's 20 cards come from species.
%
% DESIGN BRIEF: the species TRAIT already covers the body; the
% five cards cover the CULTURE. Every pool mechanizes what the
% species chapter says the people believe — Dóm grace-as-
% obligation, Squar restraint, Nol mask doctrine, Korr witness —
% so a species deck plays like a upbringing, not a biology.
%
% [PROPOSALS FLAGGED FOR AUTHOR SIGN-OFF]
%   S1. Pool size: each species pool below is its 5-card CORE
%       (at creation you take all five). Species pools grow to a
%       cap of 8 with 2–3 higher-level cards each as follow-up
%       work; no duplicates within species pools.
%   S2. Levels run L1–L2 with one L4–L5 signature per pool
%       (usually One-Shot).
%   S3. Two deliberate rule-benders, flagged inline: Serekh
%       "Patient as Stone" banks 1 Momentum across surges (a
%       species-limited exception to spin-doesn't-bank); Lemari
%       "Fruit of the Home Tree" recharges only by visiting the
%       clan-tree, not per session.
%   S4. Squar "Break the Myth" and Nol "Unmasked" write to the
%       Reputation line permanently — intended.
%   S5. Numbers are tuning placeholders, as ever.
% ============================================================

\chapter{Species Card Pools}

Your species cards are your upbringing, dealt out: not what your body does --- the trait covers that --- but what your people taught you, drilled into you, or left you to argue with. Five cards, taken whole at creation [PROPOSAL S1], and worth reading even for the species you don't play, because each pool is a culture summarized in five moves.

\medskip\hrule\medskip

\section{Frozen Coast}

\subsection{Dóm}
\textit{Grace is survival; survival is beauty; and the message arrives.}
\begin{itemize}
    \item \textbf{Clean Lines} --- 1 --- L1 --- Stance --- +1 die on Nimbleness, and moving through threatened tiles provokes nothing. No wasted motion; nothing to punish.
    \item \textbf{Carve the Slope} --- 1 --- L1 --- Move up to twice your Move across ice, snow, or descending ground, ignoring difficult terrain.
    \item \textbf{Momentum Is Form} --- 1 --- L2 --- If you moved 3+ tiles this surge, your next action gains +1 die.
    \item \textbf{No Wasted Motion} --- 1 --- L2 --- Reaction --- When an attack misses you, move 1 tile free. The miss was part of the line.
    \item \textbf{The Message Arrives} --- 2 --- L5 --- One-Shot --- Declare a destination in the scene. You reach it with this action --- over, under, along, through everything short of sealed walls --- and nothing may react to your passage. Delivery is not negotiable.
\end{itemize}

\subsection{Uln}
\textit{Heat is accounted for; disaster is met with procedure.}
\begin{itemize}
    \item \textbf{Thermal Discipline} --- 1 --- L1 --- Stance --- +2 dice on saves against heat, fire, and cold; adjacent allies gain +1.
    \item \textbf{Cold-Forged} --- 1 --- L1 --- Tune an ally's gear at the molecular grain: their weapon gains +1 die or their Armor +1 until end of scene (the benefit fails if the item is exposed to intense heat).
    \item \textbf{Measured Twice} --- 1 --- L2 --- Before making a Knack or Study roll, learn its required successes and one consequence of failure, then roll with +1 die.
    \item \textbf{Emergency Procedure} --- 1 --- L2 --- Reaction --- When a structural or environmental hazard endangers your side, negate its effects on allies within 2 tiles this round. Practiced. Coordinated. No panic.
    \item \textbf{Let It Cool} --- 2 --- L4 --- One-Shot --- Extinguish every fire and heat effect within 3 tiles; constructs and metal-bodied enemies there run cold: --1 die for the scene.
\end{itemize}

\subsection{Wyr}
\textit{Precise, recursive, and built for somewhere; memory is what endures.}
\begin{itemize}
    \item \textbf{Recursive Mind} --- 1 --- L1 --- Reroll all 1s on a Study or Investigate roll.
    \item \textbf{Recorded} --- 1 --- L1 --- Recall any scene you have witnessed with perfect fidelity; ask the GM one question of detail about it and receive a true answer.
    \item \textbf{Reboot} --- 1 --- L2 --- Clear one mental, fear, or confusion effect from yourself and heal 1 HP: a controlled restart, mid-fight, eyes open.
    \item \textbf{Cold Clarity} --- 1 --- L2 --- Stance --- In cold environments, +1 die on all Knowledge-group rolls. In hot environments this card costs 2 to play, and you resent it.
    \item \textbf{The Mark Wakes} --- 2 --- L5 --- One-Shot --- Your Maker-mark flares with original intent: negate one supernatural effect targeting you entirely, \textit{or} take 3 automatic successes on one roll. No one knows what the mark was for. Perhaps this was it.
\end{itemize}

\medskip\hrule\medskip

\section{Salt Reach}

\subsection{Gorûn}
\textit{Every pound is preparation; violence is the last tool in the pack.}
\begin{itemize}
    \item \textbf{Living Reserve} --- 1 --- L1 --- Draw on what you carry within: you or an adjacent ally clears thirst and fatigue; out of combat, heal 2 HP as well.
    \item \textbf{Broad Back} --- 1 --- L1 --- Stance --- Carry an ally or a heavy load at no penalty; +1 die on grapples while you do.
    \item \textbf{The Route Remembered} --- 1 --- L2 --- In country you have crossed before: navigation automatically succeeds, and your party treats travel hazards as one step gentler.
    \item \textbf{Last Resort} --- 1 --- L2 --- Playable only after endurance or negotiation has honestly failed (GM agrees): your first Strike this fight gains +3 dice. The desert taught you exactly when.
    \item \textbf{Written on the Body} --- 2 --- L4 --- One-Shot --- Touch the tattoo of an ordeal survived: for the scene, +2 dice on all rolls against a threat of the same kind. Permanence is reserved for truths that will not change.
\end{itemize}

\subsection{Serekh}
\textit{Slow to move, impossible to uproot; water is shared or it is nothing.}
\begin{itemize}
    \item \textbf{Stored Against Drought} --- 1 --- L1 --- Provide water for the whole party for a day, or heal yourself 2 HP.
    \item \textbf{Rooted} --- 1 --- L1 --- Stance --- You cannot be moved or knocked down, and gain +1 Defend against charging attacks.
    \item \textbf{Living Barricade} --- 1 --- L2 --- Reaction --- An attack on an adjacent smaller ally strikes your spine-hardened body instead; the attacker takes 1 hit.
    \item \textbf{Patient as Stone} --- 1 --- L2 --- [PROPOSAL S3] Bank 1 of this surge's Momentum; your side receives it on its next surge. The one exception to \textit{spin doesn't bank}, because the Serekh do not spend before it is time.
    \item \textbf{Wilt-Sight} --- 2 --- L5 --- One-Shot --- Ritual desiccation (take 2 damage): enter the oracle's fragile state and ask the GM three questions about water, weather, or what lies beneath or ahead in the land. True answers.
\end{itemize}

\subsection{Tikka}
\textit{Size is a disadvantage only for those who failed to plan.}
\begin{itemize}
    \item \textbf{Always a Bolt-Hole} --- 1 --- L1 --- Reaction --- When targeted while adjacent to cover, a crevice, or diggable ground: +2 Defend against that attack.
    \item \textbf{Scavenged Mechanism} --- 1 --- L1 --- Improvise a device from bone, chitin, and salvage: place a trap (2 hits, triggered) in an adjacent tile.
    \item \textbf{False Chamber} --- 1 --- L2 --- Misdirection: one enemy wastes its next action on you-that-isn't, or moves where you intended (a save resists).
    \item \textbf{Warren Instincts} --- 1 --- L2 --- Stance --- +1 die on Perceive against ambushes; underground or indoors, your side cannot be surprised.
    \item \textbf{The Long Preparation} --- 2 --- L5 --- One-Shot --- Reveal that you prepared this ground: place 3 traps (2 hits each) anywhere within 5 tiles you plausibly had access to. You did. Obviously you did.
\end{itemize}

\medskip\hrule\medskip

\section{Verdant Belt}

\subsection{Brindel}
\textit{The thicket is not chaos; it is a network you built.}
\begin{itemize}
    \item \textbf{Thicket-Born} --- 1 --- L1 --- Stance --- Dense vegetation is normal ground for you and +1 die to hide in; enemies pursuing you through it take 1 hit from the thorns you know and they don't.
    \item \textbf{Snare-Craft} --- 1 --- L1 --- Weave a thorn-vine snare in an adjacent tile: the first enemy entering is held (2 successes to escape).
    \item \textbf{Eye for Small Wonders} --- 1 --- L2 --- Once per scene, automatically find one hidden, small, or overlooked thing in your surroundings --- the game trail, the loose stone, the beetle worth more than the strongbox.
    \item \textbf{Read the Undergrowth} --- 1 --- L2 --- Learn the truth of this land from its small life: what passed, what nests, what's wrong here. GM answers honestly.
    \item \textbf{Ambush Ecology} --- 2 --- L4 --- One-Shot --- The thicket itself takes your side: 3 tiles of vegetation become hostile ground --- difficult for enemies, 1 hit per round to any enemy inside --- for the scene.
\end{itemize}

\subsection{Lemari}
\textit{The canopy is a country; silence means something is wrong.}
\begin{itemize}
    \item \textbf{Canopy Route} --- 1 --- L1 --- Climb and brachiate at full Move; one ally you guide ignores vertical obstacles on this move too.
    \item \textbf{Many Voices} --- 1 --- L1 --- Stance --- Your layered calls knit the side together: allies within 5 tiles gain +1 die on any roll they make with help, and your side's coordination cannot be disrupted by noise.
    \item \textbf{Third Hand} --- 1 --- L1 --- Your tail works while your hands are full: draw, stow, pass, or use an item as a free action; the held item cannot be disarmed.
    \item \textbf{Song Across Branches} --- 1 --- L2 --- Relay what you perceive: one ally in earshot gains your Perceive result, or +2 dice on their next Perceive.
    \item \textbf{Fruit of the Home Tree} --- 1 --- L5 --- One-Shot, Consumable --- [PROPOSAL S3] Eat the fruit grown from your ancestors: heal to full HP and clear every condition. It is replaced only at the clan-tree, and you will want to go home anyway.
\end{itemize}

\subsection{Silvaen}
\textit{Grown by imitation; rooted by identity; moral by hard thought.}
\begin{itemize}
    \item \textbf{Mirrored Form} --- 1 --- L1 --- +2 dice to pass as your mimicked type; while motionless among plants you are, functionally, one of them.
    \item \textbf{Rooted Recovery} --- 1 --- L1 --- Feet in soil, unmoving this round: heal 3 HP.
    \item \textbf{Learn the Shape} --- 1 --- L2 --- Watch a creature perform a physical feat: perform it yourself this scene at --1 die. (Your Master Mimics trait sharpens this further where skills apply.)
    \item \textbf{Bark and Heartwood} --- 1 --- L2 --- Stance --- +1 Armor. Fire attacks against you gain +1 die; the forest has never pretended otherwise.
    \item \textbf{The Forest Learns to Care} --- 2 --- L5 --- One-Shot --- Extend your pattern to an adjacent ally: they gain +2 Armor of living bark or a Rooted pulse (heal 3), your choice --- and you learn one true thing about what shaped \textit{them}.
\end{itemize}

\medskip\hrule\medskip

\section{High Cradle}

\subsection{Chyrr}
\textit{Complacency is a moral failure; the ambush is mercy done efficiently.}
\begin{itemize}
    \item \textbf{Always Ready} --- 1 --- L1 --- Stance --- Once per scene, when your side is surprised, you alone are not: take 1 free action before the enemy surge resolves.
    \item \textbf{Four-Armed Economy} --- 1 --- L1 --- Draw, reload, stow, and swap as free actions; brace a shield in the lower arms while both uppers work.
    \item \textbf{Strike First} --- 1 --- L2 --- Against an enemy that has not yet acted this scene: +2 dice. Hesitation multiplies risk.
    \item \textbf{Measured Withdrawal} --- 1 --- L2 --- Reaction --- When your side's surge ends, move 1 tile free, provoking nothing. An enemy routed is no longer relevant; neither is one you've stepped away from.
    \item \textbf{The Khet'kha Answer} --- 2 --- L5 --- One-Shot --- Play at the start of an encounter your side begins hidden or prepared: on your first surge, every ally's first attack gains +1 die and resolves before any enemy Reaction. Sudden. Overwhelming. Brief.
\end{itemize}

\subsection{Korr}
\textit{Forty years, spent on purpose.}
\begin{itemize}
    \item \textbf{Sprint the Sky} --- 1 --- L1 --- Fly up to twice your fly speed this action (it burns against your Athletics flight limit as normal); land at the end, hungry.
    \item \textbf{Forget Nothing} --- 1 --- L1 --- Recall anything you have personally witnessed, ever; ask the GM one question about a past scene and get the true answer.
    \item \textbf{Burning Hours} --- 1 --- L2 --- Spend the metabolism: +1 die on any roll --- then eat or rest a beat, or take --1 die next round.
    \item \textbf{Watch It Whole} --- 1 --- L2 --- Stance --- From 2+ tiles of height: +2 dice on Perceive, and allies gain +1 die against enemies you can see and call. Height is epistemology.
    \item \textbf{The Time Remaining} --- 2 --- L5 --- One-Shot --- Choose to spend it: take 2 full actions this surge for 1 Momentum total. It costs what it costs; you can feel the sunrises in it; the elders would understand, and would not approve, and would remember.
\end{itemize}

\subsection{Squar}
\textit{Anything fully known will eventually be hunted; strength is kept in private.}
\begin{itemize}
    \item \textbf{Leave No Sign} --- 1 --- L1 --- Stance --- Your passage erases itself: you cannot be tracked by mundane means, and you leave no trace others can be blamed for.
    \item \textbf{The Hidden Cache} --- 1 --- L1 --- Once per session, in wild country: declare a cache you left here, years back --- supplies, a serviceable weapon, or shelter for the party. It was always there.
    \item \textbf{Strength in Private} --- 1 --- L2 --- While no stranger observes you: +2 dice on any Strike, lift, or feat of raw power. What the myth doesn't see, the myth can't hunt.
    \item \textbf{Half Rumor} --- 1 --- L2 --- Reaction --- When enemies first see you this scene: the stories arrive before you do --- their side's next Momentum roll takes --1.
    \item \textbf{Break the Myth} --- 2 --- L5 --- One-Shot --- [PROPOSAL S4] Be seen --- fully, deliberately, terribly: every enemy who can see you saves or loses its next action. Your Reputation changes permanently, and somewhere on the hidden paths, someone will hear, and grieve.
\end{itemize}

\medskip\hrule\medskip

\section{Iron Reach}

\subsection{Barudrim}
\textit{A life without deeds worth retelling is a life unfinished; risking others for pride is unforgivable.}
\begin{itemize}
    \item \textbf{Saga-Worthy} --- 1 --- L1 --- Declare the deed aloud before attempting it: +1 die on the roll --- and if you fail, the story is still told: return this card to holstered instead of expended.
    \item \textbf{Shieldbearer} --- 1 --- L1 --- Reaction --- Reduce the hits on an adjacent ally by 1; you take 1. That is what the shoulders are for.
    \item \textbf{Laugh at Fear} --- 1 --- L2 --- Stance --- You and allies within 3 tiles gain +2 dice against fear and despair; also, you are singing, and nobody is sneaking anywhere.
    \item \textbf{Carry Them Out} --- 1 --- L2 --- Lift an ally --- downed included --- and move your full Move. The old rest. The young grow. That was always the point of the strength.
    \item \textbf{The Unfinished Life} --- 2 --- L5 --- One-Shot --- At 0 HP or dying: rise to half HP for the rest of the scene. If the fight is worthy, you may hear, faintly, the verse being composed.
\end{itemize}

\subsection{Human}
\textit{Rarely the strongest. Reliably the last to give up.}
\begin{itemize}
    \item \textbf{Second Wind} --- 1 --- L1 --- Heal 2 HP and clear fatigue. Once per scene; the well is deep, not bottomless.
    \item \textbf{Fast Learner} --- 1 --- L1 --- After failing a roll, gain +2 dice on your next attempt at the same task. The second try is the human art form.
    \item \textbf{Jack of the Frontier} --- 1 --- L2 --- Treat one skill you have 0 rating in as rating 2 for the scene. You've watched this done. How hard can it be. (Hard. Do it anyway.)
    \item \textbf{Persistence Hunter} --- 1 --- L2 --- Stance --- Against anything fleeing you: +1 Move, and your side's pursuit rolls gain +1 die. You will not tire first. You have never tired first.
    \item \textbf{One More Mile} --- 2 --- L4 --- One-Shot --- The oldest human trick, worked on your friends: your whole side clears fatigue, heals 1 HP, and gains +1 Move for a scene --- because you kept going, and made stopping embarrassing.
\end{itemize}

\subsection{Mairin}
\textit{Stability is survival; grief ripples; someone must carry the preparations.}
\begin{itemize}
    \item \textbf{The Deeper Pack} --- 1 --- L1 --- Once per scene, produce the \textit{specific} mundane item this moment needs, worth up to 3 Rings. (Your species trait covers the everyday; this is the once-a-crisis miracle of foresight.)
    \item \textbf{The Careful Larder} --- 1 --- L1 --- Consumable ×3 --- Preserved rations, properly done: spend to heal 1 HP and clear hunger or fatigue.
    \item \textbf{Measured Risk} --- 1 --- L2 --- Before an ally rolls: warn them what you see. They may abandon the action (Momentum refunded) or proceed with +1 die.
    \item \textbf{Steady the Ripple} --- 1 --- L2 --- Reaction --- When fear, grief, or a morale effect strikes an ally: negate it. You take --1 die on your next roll; you are carrying it, the way your people always have.
    \item \textbf{Everything in Its Place} --- 2 --- L5 --- One-Shot --- Reveal that you prepared for \textit{this exact disaster}: the party gains 3 tokens, each spendable once for: heal 2, +1 die on a roll, or negate one environmental hazard.
\end{itemize}

\subsection{Nol}
\textit{The mask was a prayer before it was a threat; fear, carefully cultivated, is a shield.}
\begin{itemize}
    \item \textbf{The Mask Forward} --- 1 --- L1 --- Stance --- +2 dice on Intimidate, and predators of the unseen world --- things that hunt by familiarity, name, or memory --- take --1 die targeting you. The old purpose still works.
    \item \textbf{Ritual Laughter} --- 1 --- L1 --- You and allies within 3 tiles gain +1 die against fear and despair; enemies hear it and are invited to wonder what, exactly, is funny.
    \item \textbf{Loom Larger} --- 1 --- L2 --- Your silhouette does the arguing: one enemy saves or will not willingly come within 2 tiles of you until you attack it.
    \item \textbf{We Are Not Unreasonable} --- 1 --- L2 --- Deliver terms from behind the mask: enemy morale rolls to keep fighting take --1 die for the scene, and any surrender your side accepts, your side honors. That second clause is the whole reputation.
    \item \textbf{Unmasked} --- 2 --- L5 --- One-Shot --- [PROPOSAL S4] Take it off. Before one creature, deliberately: honest face, honest words. Its hostility toward you ends unless it saves --- and either way, it has met the person, and your Reputation with everyone who hears of this changes accordingly. The strongest card in the pool is the one where you stop.
\end{itemize}

\subsection{Pelorim}
\textit{Identity is the routes you keep; forgetting a path is a moral failure.}
\begin{itemize}
    \item \textbf{The Way Is Known} --- 1 --- L1 --- Declare you have walked this kind of route: navigation automatically succeeds and the party gains +1 die against its characteristic hazards.
    \item \textbf{Courier's Gait} --- 1 --- L1 --- Stance --- +1 Move, and a rider you carry may act freely while you move: you are the road and the wagon both.
    \item \textbf{Never Linger} --- 1 --- L2 --- Reaction --- Against anything that would hold, root, or slow you: save with +2 dice, and on success, move 1 tile free. Stillness is how ways die.
    \item \textbf{The Wider Web} --- 1 --- L2 --- Once per session: name someone along the routes who owes the ways a favor --- a station master, a Gorûn elder, a Warden at a relay. The GM makes them real and reachable.
    \item \textbf{Forward} --- 2 --- L5 --- One-Shot --- Invoke the oldest obligation: for one scene, your side ignores difficult ground and gains +1 Move while moving \textit{toward} its goal --- and you cannot retreat while it holds. The routes go one direction. That was always the deal.
\end{itemize}

\medskip\hrule\medskip

\section{Table Notes}

\textbf{Five cards, one thesis.} Each pool is built to state its people's argument in play: the Dóm pool is grace spent on others' urgencies, the Squar pool is power hidden until hiding costs too much, the human pool is five flavors of \textit{not stopping}. When these cards come up at the table, the culture is present in the room --- which is why the species pools stay small: seasoning, not the meal.

\textbf{The capstones are choices, not upgrades.} Nearly every L4--L5 signature asks the character to spend something the culture holds dear --- the Korr's hours, the Squar's myth, the Nol's mask, the Mairin's composure, the Serekh's own body. Players who reach for them should feel the species chapter looking over their shoulder, and GMs should let the aftermath land: \textit{Break the Myth} and \textit{Unmasked} write to the Reputation line in ink.

\textbf{Growth room.} [PROPOSAL S1] These are the 5-card cores; each pool wants 2--3 more cards at L3--L7 in the follow-up pass (the Wyr have more marks than one; the Gorûn have more tattoos), holding the cap at 8 so species never competes with class for a deck's center of gravity.
