% ============================================================
% ACADEMIC ENCLAVES — REWRITE
% ------------------------------------------------------------
% CANON DECISIONS PROPOSED IN THIS FILE (all revisable):
%   - Spellbooks as reliquaries: a dying Arcanist's accumulated
%     arcane mass migrates into their spellbook if present. Books
%     therefore carry generations of the dead, grow more potent
%     (and faintly awake) with age, and are the Enclaves' true
%     inheritance. Untended deaths leave "residue" — site hauntings.
%     This retro-justifies: the book economy, the Burning Library's
%     nature (they carry their dead), and why the Kindling was
%     unforgivable (burning books = burning the dead).
%   - The Vellhame Convocation: the inter-Enclave assembly (every
%     seven years) created after 189 SR to set containment
%     protocol. Enforcement: reputation + Lions leverage.
%   - Internal offices: the Attendance (deathbed logistics) and the
%     Office of Returns ("Retrievers") — rogue-Arcanist recovery.
%     A Registry writ on an Arcanist means Returns has given up on
%     alive.
%   - Ranks: Foundling -> Candidate -> Adept -> Magister -> Rector
%     (head of an Enclave); Convocation seats held by Rectors.
%   - Named Enclaves: Thirstgate Tower (urban/political; Rector
%     Wren Fadlock, liaison Caesius Mark — from notable-factions),
%     Northwatch (frontier research; Rector Halvi Snow, Warden
%     exchange — from notable-factions), the Burning Library
%     (itinerant — from notable-factions), the Amaranth Hall (NEW:
%     oldest, theoretical, arrogant), the Endline Charter (NEW:
%     young, pragmatic, fast-training, Company-adjacent).
%   - The Fey question: three in-world positions on magic's origin
%     (the Debt, the Many Wells, the Mirror). The Enclaves' public
%     silence is doctrine. The Wyr data point: no recorded Wyr
%     eruption, ever — evidence claimed by all three camps.
%   - Cross-refs: Timeline (Vellhame 189, Kindling 211), Lions
%     rewrite (Library records offer, regional doctrine), Houses
%     rewrite (Vehk petition = Thirstgate Tower's; post-Talvecq
%     refusal doctrine), regions.tex, cosmology.md.
% ============================================================

\section{The Academic Enclaves}

\subsection{Origins}

Arcane magic is not learned. It erupts.

It arrives unasked, in childhood or adolescence, in perhaps one person in several thousand, without regard for lineage, station, species, or desire --- with a single, total exception discussed later in this chapter --- and it arrives as a problem. The manifesting child does not receive power the way an heir receives a gift. They receive a pressure: heat that answers anger, light that answers fear, the fabric of near reality flinching in sympathy with a mind that has not yet learned that reality is listening. An untrained eruption is not dramatic at first. It is small wrongnesses accumulating --- scorched bedding, milk soured in a sealed jug, a dog that will not enter the room --- in a community that has, for a hundred and twenty years, known exactly one word for where small wrongnesses lead.

The word is Vellhame.

In 189 SR, a senior Arcanist of the Vellhame Enclave --- careful, credentialed, beloved by his students, every account agrees --- suffered an accumulation cascade that neither he nor his colleagues arrested in time, and the town of Vellhame, population somewhat over three thousand, was unmade in an afternoon. Not burned. \textit{Unmade}, in ways the relief expeditions spent years failing to describe consistently. Vellhame is why the frightened village and the forming mob are not ignorant superstition but a folk memory with a date on it; why the Enclaves rebuilt their standing across the following century through protocol, transparency, and demonstrated usefulness; and why every Enclave in the known regions maintains the institution on which all the others rest: \textbf{the informant network} --- the paid, protected, quietly heroic web of midwives, schoolteachers, Circuit Riders, tavern-keepers, and grandmothers who know what small wrongnesses look like, and who get word to the Enclave \textit{before} the community gets to the older solution.

So the founding scene of the whole tradition, repeated a thousand times a generation, is this: a rider arrives in a village that has begun to be afraid, and a child who did not ask for any of it is offered the only real choice their eruption left them --- and leaves. The Enclaves are honest with themselves about what this is. It is a rescue, and it is a removal, and the fact that it is genuinely both is the institution's first lesson in its own nature. Everything the Enclaves are --- the walls, the protocols, the usefulness, the distance --- descends from the terms of that departure: \textit{we will take the danger away from you, and in exchange you will let it live.}

An Enclave, then, is four things wearing one building. It is a school, because the untrained are catastrophic. It is a containment, because the trained are merely dangerous. It is a research institution, because the discipline's central questions remain open. And it is an embassy, because the surrounding society's tolerance is the load-bearing wall, and tolerance --- as the Enclaves teach their Foundlings frankly, in those words --- is revocable. The safest Enclaves are not the most feared. They are the most \textit{useful}: the ones whose wards keep the town's granaries dry, whose Adepts ride with the caravans, whose Rector is owed too many favors to burn. Usefulness is the rent, and the Enclaves pay it with the discipline of institutions that have read their own history.

\medskip\hrule\medskip

\subsection{The Mass and the Book}

What erupts does not go away. This is the discipline's first fact and its whole predicament.

The working term is \textbf{arcane mass}: the substance --- state, condition; the vocabulary is admitted to be a placeholder --- that accumulates in a practitioner across a working life. Every casting deposits; nothing withdraws. The mass is why an old Arcanist is more powerful than a young one in ways that have nothing to do with knowledge, why power and danger are the same curve, and why the discipline's core teaching is not spellcraft but \textit{stewardship}: pacing, grounding, the accountancy of a self that is becoming, gram by gram across the decades, something that the self is required to carry and forbidden to put down.

Except once.

What the Enclaves learned --- early, empirically, at the cost of incidents their archives record with great care --- is what the mass does at death. Untended, it does not disperse. It \textit{seeks}: pools in the deathplace, soaks into ground and timber, and produces the phenomena the rural regions call residues and the Enclaves call, in the flat taxonomy of people determined not to be poetic about it, \textbf{unhoused mass} --- cold rooms, recurring lights, the specific bad luck of buildings where an Arcanist died alone. But if the Arcanist's \textit{spellbook} is present at the death --- the working book, the decades-long companion document of the practitioner's craft --- the mass goes \textit{there}. Cleanly, completely, and by a mechanism that remains, like most true things in this discipline, unexplained.

Understand, then, what a spellbook is. It is not notes. It is the vessel of everyone who has ever died holding it. The books are inherited --- master to student, generation to generation --- and each inheritance adds a life's accumulation to the vessel, so that the great old books of the tradition, the ones with forty names in the front matter, are the most potent artifacts the Enclaves possess: dense with the banked mass of centuries, easier to work great craft through than any young book, and --- every Arcanist who has kept one long enough says the same thing, in the same reluctant tone --- \textit{faintly awake}. Not minds. The Enclaves are firm, publicly, that the books are not minds. They are described, in the private registers, as having weather.

From this one fact, most of the tradition's strange economy follows. Why the books are chained --- to desks, to belts, to the wrist in the field --- in the old library manner. Why book-theft is the crime the Enclaves pursue across any distance and never forgive; why a forged lineage-book is worth a fortune and a death sentence; why the estate of a dead Arcanist is a legal specialty; and why every Enclave maintains \textbf{the Attendance} --- the office, equal parts hospice and honor guard, that ensures no member of the community dies out of reach of their book. Attendance duty is the most solemn work an Adept is assigned and the most quietly formative: you sit the deathwatch, you place the book in the failing hands, and you learn, at the bedside, exactly what it is you have agreed to become.

And understand, finally, what the Burning Library is. When the Candlevault burned in 211 SR, what burned was not an archive. It was the housed dead of the eastern tradition --- generations of banked lives, unmade in a night by ordinary fire. The survivors' vow never again to keep what can be destroyed is not eccentricity. The Library walks because it is a funeral that was never allowed to end, and it carries its remaining books on its people's bodies, chained, always, and it has spent a century being unfailingly polite to the institution it believes lit the fire.

\medskip\hrule\medskip

\subsection{The Question}

Where does it come from?

The Enclaves do not answer. This is doctrine, formalized by the Convocation and held with a unanimity the Enclaves achieve on almost nothing else, and the public reason is the honest one: \textit{the discipline does not know}. But the shape of the silence is informative, because the question has three serious answers, and the Enclaves' refusal to rank them in public is not the same as having no opinions in private.

\textbf{The Debt.} The oldest scholarship holds that magic entered the world through bargain with the Fey --- the inhabitants of the Wyrd, whose dealings are the oldest in existence --- and that the price of the bargain has never been identified, which is not the same as never having been paid. On this reading, every eruption is an installment: the debt collecting itself, child by child, through a mechanism the original parties would recognize and no living person does. The Debt reading explains the discipline's worst fact --- that eruption is unasked, unearned, and unrefusable --- with terrible elegance. It is also, its critics note, exactly the kind of story that would profit the Fey to have believed, which brings us to:

\textbf{The Mirror.} The Fey grow stronger on the legends mortals tell --- this is not theory but observed mechanics of the Wyrd --- and the Fey-origin story is itself a legend, old, potent, and endlessly retold. The Mirror reading holds that the Debt is Fey propaganda: a story planted precisely because a debt believed is a leverage owned, and that the true origin lies elsewhere while the Wyrd feeds, quietly, on the fear of a price that was never real. The Mirror reading's difficulty is that it cannot be distinguished, from inside, from the thing it describes --- a problem its own proponents concede with a certain professional admiration.

\textbf{The Many Wells.} The empiricist position: that ``arcane magic'' may not be one thing with one source at all, that eruption statistics vary by region, era, and proximity to boundary phenomena in ways no single-origin account survives, and that the discipline should stop asking \textit{where the river starts} and start mapping tributaries. The Many Wells camp runs the field stations, maintains the eruption censuses, and produces most of what the discipline actually knows, while being accused by both other camps of answering the question by declining to hear it.

One datum is claimed by all three camps, and it is the exception flagged at this chapter's start: \textbf{no Wyr has ever erupted.} Not once, in the entire recorded span, in the one people who were \textit{made} rather than born --- constructed minds, Material artifice, the children of vanished Makers. The Debt reads it as proof the bargain binds bloodlines and the Wyr have none. The Mirror reads it as proof the phenomenon routes through the dreaming and the Wyr do not dream. The Many Wells reads it as the single best experimental control in the discipline's possession and has been trying, politely and unsuccessfully, to get a Wyr research cohort funded for thirty years. The Wyr themselves, asked their opinion, tend to reply that they find it restful to be the one people whose relationship with magic is entirely voluntary --- an answer that is not data and is remembered longer than most data.

Why the public silence, then? Because of the Lions. Because a discipline that cannot say where its power comes from is tolerable, and a discipline that says \textit{it may come from an unpaid bargain with the Wyrd} is, in the hard-doctrine regions, a confession with a date to be set. The Enclaves' critics have always said the silence \textit{is} the confession. The Enclaves' position, stated once per generation and otherwise lived, is that they will not teach dread as fact --- and that if the day comes when the question is answered, they intend to be the ones holding the answer, because they have seen what everyone else does with fear.

\medskip\hrule\medskip

\subsection{Structure}

An Enclave is a community of perhaps forty to four hundred, organized in a rank ladder the whole tradition shares.

\textbf{Foundlings} are the arrivals --- the escorted children, the occasional manifesting adult --- in the first years of grounding and stabilization, during which they are not taught craft at all: they are taught \textit{stillness}, accountancy of the self, and the protocols, in that order. \textbf{Candidates} have stabilized and begun the craft proper, under supervision, in warded halls. \textbf{Adepts} are the working tradition --- credentialed, field-cleared, the Arcanists a town actually meets: ward-wrights, caravan-riders, field researchers, Attendance-sitters. \textbf{Magisters} carry mastery and its weight: teaching chairs, containment authority, the deep research, and the accumulating mass that makes each of them, by the discipline's own arithmetic, a larger fact than they were. A \textbf{Rector} heads an Enclave --- elected by its Magisters in most charters --- and holds its seat at the \textbf{Convocation}: the assembly of Rectors, convened every seventh year since 196 SR in the shadow of Vellhame, that sets the containment protocols, accredits new Enclaves, and holds the only powers the whole tradition answers to. The Convocation commands no troops and owns no buildings. What it owns is standing: an Enclave struck from the Convocation's registry loses its informant funding, its graduates' credentials, its neighbors' tolerance, and, in short order, its existence. It has struck three in a century. The tradition can name all three without pausing.

Two offices exist in every registered Enclave, and they are the two the outside world knows least and should know best.

\textbf{The Attendance} has been described: the deathwatch office, hospice and honor guard, keeper of the register of the dying. Its seniors are, by long custom, the most trusted members of any Enclave --- the phrase \textit{fit to sit an Attendance} is the tradition's highest ordinary compliment.

\textbf{The Office of Returns} is the other thing, and the tradition's grimmest necessity. Arcanists leave. Some walk out untrained; some walk out trained and unwilling; some do not walk so much as \textit{drift}, the stewardship failing by degrees until the person and the accumulation trade places. The Office of Returns --- its field agents are called Retrievers by everyone except their own paperwork --- exists to bring them back: preferably persuaded, acceptably compelled, alive as an absolute priority that the office's charter states in language of unusual force, because a rogue Arcanist who dies afield dies away from any book, and the office's true mandate is not discipline but \textit{housing} --- of the person if possible, of the mass regardless. Retrievers work in pairs, carry a bonded retrieval book among their equipment, and hold the discipline's most honest job description: \textit{we are sent after the ones the rescue did not take.}

When Returns exhausts itself --- when persuasion has failed, compulsion has failed, and the subject's trajectory has been formally judged to be Vellhame-shaped --- the Enclave does the thing it hates most: it posts a writ. A Registry bounty on a named Arcanist is therefore one of the rarest documents in the writ system and the most instantly understood. It means an Enclave has concluded, through its most reluctant process, that \textit{alive} is no longer the priority --- and every certified Hunter who has ever taken one describes the same detail: the Enclave pays promptly, in full, and asks the hunters, always, whether the book was recovered, in a tone that makes clear which death they are grieving.

\medskip\hrule\medskip

\subsection{Signs and Rites}

An Enclave announces itself to the nose before the eye: ozone and cold stone, beeswax and old paper, the mineral tang of ward-chalk --- the weather of banked mass, which visitors describe as the feeling of a storm that has decided to be patient. The architecture runs to thick walls, interior courtyards, and the \textbf{quiet halls}: the warded working spaces where Candidates train, in which sound behaves conservatively and visitors are asked, in signage of perfect courtesy, not to be surprising.

Members wear \textbf{the grey} --- slate-grey over-robes, unadorned at Foundling, edged in the Enclave's color from Adept --- less as uniform than as courtesy: the grey tells a nervous room what it is looking at, which the Enclaves long ago concluded is safer than being wondered about. The chained book completes the figure; an Arcanist's rank, lineage, and rough age can be read by the trained eye from the book alone --- its size, its wear, the count of clasps --- and the tradition's private etiquette runs through books the way House etiquette runs through the body: one never touches another's book, never asks its names unoffered, and never, under any sky, remarks that a book seems \textit{heavy today}, a phrase reserved for funerals.

The rites are the Attendance's: the deathwatch, the placing of the book, and the \textbf{Reading of Names} --- once a year, each Enclave, aloud, the front-matter of every book in its keeping, oldest first, which in the Amaranth Hall takes three days and in a frontier charterhouse takes one grave hour. Foundlings attend their first Reading within a month of arrival. The tradition's view is that a child who has just lost one home should hear, immediately and at length, exactly how long the new one remembers.

Speech: an eruption in the wild is a \textbf{kindling} (the word predates 211 SR, and the Library's people use it anyway, with a flat look that ends conversations); to die attended is to be \textbf{housed}; a rogue is \textbf{out}, an unrecovered rogue is \textbf{weathering}; and the discipline's all-purpose benediction, said at partings, bedsides, and the doors of the quiet halls, is \textit{``carry it well.''}

\medskip\hrule\medskip

\subsection{The Enclaves}

Perhaps sixty registered Enclaves hold Convocation seats. These five span the tradition's range, and a campaign will feel their differences within an hour of the gate.

\subsubsection{The Amaranth Hall --- the Old Weight}

The oldest continuously chartered Enclave in the known regions --- its founding predates Standard Reckoning, its Reading of Names takes three days, and its cellars hold books whose front matter runs past sixty names into hands no living scholar can date. The Hall is theoretical, wealthy, magnificent, and arrogant in the institutional manner of something that has outlived every criticism: it trains slowly and superbly, publishes the discipline's foundational work, dominates the Convocation's protocol committees, and regards the frontier charterhouses with the affection of a cathedral for a tent revival. Its unspoken burden is its cellars: the Hall holds more banked mass than any three other Enclaves combined, its eldest books have \textit{weather} that the junior librarians request transfers over, and the Convocation's most carefully unminuted discussion, each seventh year, is what the Hall's holdings will someday require of everyone else.

\subsubsection{Thirstgate Tower --- the Embassy}

The political Enclave: seated in the largest fortified settlement in the Iron Reach, three streets from the Lions' operational headquarters, and run accordingly. Rector \textbf{Wren Fadlock} --- Lemari, canopy-born, sixty years from her clan's trees and fluent in every institutional dialect the Reach speaks --- has made the Tower the tradition's diplomatic instrument: its Adepts ward the town's granaries and the rail yards, its liaison office practically shares a wall with the Lions' chapter house, and its senior liaison, Magister \textbf{Caesius Mark}, has spent twenty years turning the Enclave--Lions relationship from doctrine into acquaintance --- he attends the chapter's public Vigils, Banneret Vairo attends the Tower's Reading, and both institutions understand precisely how much load those courtesies carry. It is the Tower that filed the petition to study the Vehk expression: respectful, scientifically impeccable, and --- Fadlock has been slow to grasp this, her critics say, or has grasped it perfectly, her admirers say --- the respectable channel through which every less respectable appetite in the south is now pressing.

\subsubsection{Northwatch --- the Field Station}

The frontier research Enclave: small, cold, brilliant, perched at the Frozen Coast's edge where the boundary phenomena come to it. Rector \textbf{Halvi Snow} is Wyr --- a mind that runs clearest exactly where the postings are worst, and the living emblem of the tradition's strangest datum, a Rector of the arcane who cannot, personally, erupt. Under Snow, Northwatch runs the discipline's only formal research exchange with the Frontier Wardens --- boundary observation for containment expertise, renewed annually, envied by every Many Wells station in the registry --- and hosts the Wyr-cohort question at every Convocation, where it is thanked, praised, and not yet funded. Northwatch's Adepts are the tradition's field breed: competent at sledge-craft and rescue, on first-name terms with Warden relay posts, and possessed of the particular humor of people who study the thin places by living on one.

\subsubsection{The Burning Library --- the Funeral That Walks}

Itinerant since 211 SR; described above, and never adequately. The Library is small --- perhaps ninety souls at any census, though its census is nobody's business --- and it travels in reading-wagons and rented halls, trading the finest bibliographic and archival expertise in existence for provisioning, protection, and the standing right to copy. Its members chain their books waking and sleeping; its seniors, the \textbf{Readers}, carry the salvaged elders of the Candlevault, books of terrible weight and gentle weather; and its century of scrupulous, unfailing politeness toward the Witnesses of the Lion has been, all parties understand, the longest sustained act of accusation in the world. Last year, on the Kindling's centennial, the Library stood a silent night in Thirstgate within sight of the Lions' seat --- and this year, for the first time, its Readers have offered to open the survivors' records of the burning, in exchange for the Lions' own records of the same decade. The tradition is holding its breath. The Library has waited a hundred years; it can wait for an answer.

\subsubsection{The Endline Charter --- the New School}

Twenty-two years chartered, seated in the Salt Reach's rail-head bustle, and everything the Amaranth Hall fears the tradition is becoming: fast, pragmatic, solvent, and unembarrassed. The Charter trains working Adepts in half the Hall's time, places them with Companies, caravans, and settlements on service contracts that fund the whole enterprise, and answers criticism of its pace with its safety record, which is --- this is the maddening part, the Hall's committees agree --- excellent. Its Rector, a former Retriever named \textbf{Odessa Vance}, runs the registry's most aggressive informant network on the theory that the frontier's manifesting children cannot wait for beautiful pedagogy, and the Charter's real argument with the old tradition is underneath the pace: Vance trains stewardship as a \textit{trade}, not a vocation, and whether the discipline can survive being ordinary is a question the Convocation has tabled twice and will not table a third time.

\medskip\hrule\medskip

\subsection{The Enclaves Among the Factions}

\textbf{The Lions} are the relationship, singular --- the weather in which every Enclave lives. The mainline's century of working coexistence (liaison offices, shared Vigils and Readings, the Tower--chapter acquaintance) and the Unblinking's standing question (what \textit{is} it, and what does it owe) divide the map into regions where an Adept's grey is a credential and regions where it is a target's outline. The Kindling sits under all of it, unresolved by design of no one and to the convenience of no one, and the Library's records offer has just made the oldest wound in the relationship, briefly, a door.

\textbf{The Noble Houses} and the Enclaves circle a single fact from opposite sides: heritable, expressed capability against erupted, unheritable capability --- the Houses' power arriving by blood and worn on the body, the Enclaves' arriving by lightning and carried in the book. The research appetite is real, respectful, and refused; after the Cascade, the Concord's doctrine on the study of gifts is not curiosity but dread, and the Enclaves --- who of all institutions best understand watching a capability outrun its steward --- press the point with a gentleness their own researchers find maddening. The Vehk petition is the live case, and both signatories to that sentence know it is not really about the Vehk.

\textbf{The Guilds} meet the Enclaves twice: in the Sawbones halls, where containment medicine, eruption trauma, and the physiology of accumulation are a shared literature two proud institutions pretend they are not co-writing; and in the Tinkerers' works, where the polite fiction that arcane craft and vim engineering are unrelated disciplines is maintained by everyone and believed by no one under Magister rank.

\textbf{The Companies} operate the useful-Enclave doctrine from the demand side: ward contracts, caravan Adepts, survey consultancy, and --- growing, and watched with unease by the Convocation --- the Endline model of service-contract training. A Company town with a charterhouse is measurably safer and marginally owned, and which institution is renting which is a question the Charter's critics ask loudly and its ledgers answer ambiguously.

\textbf{The Wardens} and the Enclaves share exactly one deep channel --- Northwatch --- and a broad shallow one: the informant networks overlap in the field, and a Warden who finds a manifesting child three weeks from anywhere has, more than once, made the walk. The traditions are temperamentally opposite (the Wardens supplicant before what they do not control; the Enclaves stewards of what they cannot refuse) and get along, in the field, rather better than either's doctrine predicts.

\textbf{The Registries} hold the Enclaves' most reluctant account: the rogue writs, rare, unmistakable, and paid in full with one question asked after. Between writs, the relationship is procedural and oddly warm --- Registry adjudicators like institutions that document everything, and the Enclaves document \textit{everything}.

\medskip\hrule\medskip

\subsection{Current Fault Lines}

\begin{itemize}
    \item \textbf{The Petition Coalition.} Thirstgate Tower's respectful request to study the Vehk expression has become the channel through which Company survey interests and a Lions ``interpretive access'' request now flow in coordination --- coordination the Tower did not seek, cannot control, and is being blamed for. Karim Vehk's hired investigators are pulling threads that lead, embarrassingly, toward the Tower's own liaison office, and Caesius Mark has begun to suspect his twenty years of acquaintance are being spent by someone else, for something else.
    \item \textbf{The Library's Offer.} Records for records, wound for wound. If the exchange happens, the Kindling gets an answer at last --- and the tradition has noticed that the Library, which never does anything without three reasons, has chosen to make the offer in the exact season the Lions' succession makes every archive a weapon.
    \item \textbf{The Weathering of Magister Corvin.} The discipline's worst live case: a Magister of the Amaranth Hall --- Attendance-fit, protocol-perfect, forty years of exemplary stewardship --- walked out of the Hall eleven months ago without his book, which is not done, is not \textit{possible} by the Hall's own wards, and has not been explained. Returns has fielded four pairs. Two came back persuaded of nothing, and two came back \textit{unsettlingly persuaded} --- of what, their debriefs do not agree. No writ has been posted. The Convocation's protocol committee has asked the Hall, in writing, why not, and the Hall's reply is three weeks late.
    \item \textbf{The Hidden Incident.} Somewhere in the registry --- the eruption censuses make the statistical case plainly, the Many Wells stations having done their work too well --- an Enclave is under-reporting containment events. The Convocation knows \textit{that}; it does not know \textit{which}; and the instrument it would normally use to find out --- reputational pressure through the registry --- is the very thing an under-reporting Rector is hiding from. Quiet outside hires have been authorized for the first time since the office of Returns was founded.
    \item \textbf{The Charter Question.} Endline's model works, spreads, and cannot be un-invented: three new applications on its pattern sit before the Convocation's next session. If stewardship becomes a trade, the tradition survives by becoming ordinary; if the Convocation refuses the applications, the frontier will simply train outside the registry, which is how the discipline's history began and the one way everyone agrees it must not end.
\end{itemize}

\medskip\hrule\medskip

\subsection{The Enclaves in Play}

\textbf{Playing Enclave blood --- there is none.} That is the point, and the character hook. An Arcanist PC was a Foundling once: somebody's child, in somebody's village, on the day the rider came. The tradition claims them the way a rescue claims --- by debt of gratitude rather than blood, which binds some people far tighter and others not at all --- and every Arcanist carries the eruption's social inheritance: the grey that must be worn, the book that must be chained, the hometown that may or may not want the letter they keep not sending. Rank maps cleanly to tier: a field-cleared Adept is the classic adventuring Arcanist; a Magister carries enough banked mass to be a strategic fact; and the campaign question the tradition hands every one of them is the stewardship curve itself --- \textit{you will spend your whole life becoming more of exactly the thing you must keep carrying.}

\textbf{What the Enclaves pay adventurers to do.} Constantly, and for structural reasons: the tradition's own members are its most regulated resource, and half its necessary work is work an Adept in the grey cannot do quietly. Typical contracts, by tier:

\begin{itemize}
    \item Escort an informant's letter, or the rider answering it, to a village that has begun to be afraid --- and arrive before the older solution does.
    \item Guard an Attendance: a Magister is dying three weeks from her Enclave, the book must reach the bedside, and the road knows what the book is worth.
    \item Recover a stolen book before its buyer learns to open it --- or a forged one before its lineage is believed.
    \item Sit the perimeter of a residue --- an unhoused death-site --- while the housing team works, and handle what the weather attracts.
    \item Support a Returns pair on a retrieval: the Retrievers handle the subject; the party handles everything the subject's weathering has gathered around them.
    \item Investigate, on the Convocation's quiet contract, which Enclave in a given region is lying to the registry --- work that pays triple and explains why at the first gate.
    \item Take the writ nobody wants: a named Arcanist, a Registry seal, an Enclave's grief priced into the fee --- and the standing bonus, always, for the book.
    \item At the highest tiers: escort the Library's Readers to the records exchange, through every party that prefers the wound open; or find Magister Corvin, who left without his book, and learn what four Retriever pairs could not agree they saw.
\end{itemize}

\textbf{Patrons.} \textit{Magister Caesius Mark} --- the Tower's liaison buys discretion by the season: escorts, inquiries, and increasingly, this year, investigations he cannot route through his own office because his own office is what he is investigating. \textit{Rector Halvi Snow} --- Northwatch contracts the tradition's best fieldwork: boundary surveys, relay support, and the occasional walk out onto the ice with instruments, a Warden, and instructions that begin \textit{whatever you observe, write it down before you discuss it}. \textit{A Reader of the Burning Library} --- the Library pays in copies, introductions, and the finest research support in existence, and its contracts have a single non-negotiable clause, which is that the books come back. There has never been a second clause. There has never needed to be.

\medskip\hrule\medskip
