% ============================================================
% BOUNTY REGISTRIES — REWRITE (psychic Hunter revision)
% ------------------------------------------------------------
% AUTHOR DIRECTION IMPLEMENTED:
%   - The Bounty Hunter is the setting's other psychic class:
%     where the Orders' Eye works the collective unconscious
%     broadly, the Hunter attunes to the unconscious of ONE
%     individual — the quarry. Rogue equivalent.
%   - One Registry founded/captured by an outcast of House
%     Corvara who has SPREAD vampirism to its hunters — the hunt
%     as another way of getting prey.
% CANON DECISIONS PROPOSED (all revisable):
%   - The Read: dream-tracking, not mind-entry — the unconscious
%     sheds into the dreaming; Hunters read the shed wake
%     ("we don't open doors; we read footprints"). This earns the
%     Orders' grudging Closed Door ruling and keeps the class
%     rogue-flavored (a tracker in the dream-medium).
%   - The writ system retro-justified by the art: writs demand
%     true names and void on error because the Read requires the
%     name. Relics (possessions, writing, blood) deepen the Read.
%   - Countermeasure weld: Nol masks baffle the Read (they were
%     made against "predators that hunt by familiarity").
%   - Effacement: the registries' damnatio memoriae — a voided
%     name cannot be written on a writ, and therefore cannot be
%     Read. THE EFFACED: the legendary uncaught target, an
%     ex-Provost of the struck Verge Registry (289 SR), made
%     unhuntable by his own punishment.
%   - The vampiric registry: the Long Table at Dustline; its
%     inner circle, the Night Bench, built by MAREN CORVARA
%     (struck from the blood-book ~30 years ago for transmission
%     research — she is the unstated subject of the Corvara's
%     "the House does not discuss its research"). Transmitted
%     vampirism: weaker gifts than born Dynasts, crueler thirst,
%     no tithe infrastructure — so the writ IS the feeding. The
%     dark synergy: for a vampiric Hunter, tasted blood is the
%     perfect relic — feeding deepens the Read.
%   - Named registries: Thirstgate (the model), Lastlight (holds
%     the Corvenwood bounty), Greywater (admiralty/arbitration),
%     the Long Table at Dustline.
%   - The Corvenwood killings (Houses rewrite) are left joinable
%     to the Night Bench: the trail runs east.
%   - Cross-refs: Mercenary rewrite (the bare, Convention panels,
%     Jackal writs), Houses (Corvara, Transfusion Question),
%     Orders (Closed Door), Enclaves (rogue writs), species (Nol),
%     timeline.
% ============================================================

\section{The Bounty Hunter Registries}

\subsection{Origins}

Every other institution in this book exists to keep promises. The Registries exist for the moment a promise runs out of world.

A stateless order handles most wrongs surprisingly well, through the machinery the other chapters describe: the defense paper answers violence, the arbitration compacts answer disputes, the Guild marks answer fraud, the demesne stones answer trespass. What none of that machinery can answer is the person who \textit{leaves} --- who does the harm and steps outside every web that could bill him for it: off the client rolls, past the demesne stone, beyond the reach of any Company's paper, into the enormous ungoverned distance that is most of the world. The insurers' term for such a person is \textbf{bare}, and the term is precise: uncovered, unanswerable --- and, the early frontier learned, effectively \textit{invisible}, because a world without census, border, or comprehensive map is a world where a man who changes towns has very nearly changed souls.

The Registries were built backward from the people who could find him anyway.

They have always existed --- the trackers of last resort, the ones hired when the trail was cold and the name was all that remained --- and the frontier's oldest stories about them record, with unease, that the best of them worked in ways the word \textit{tracking} did not cover: hunters who took a name and a stolen keepsake and rode, not following sign, but \textit{converging}; who slept badly on the hunt and woke knowing things; who spoke, at the end, to men they had never met with the terrible familiarity of an old friend calling in a debt. The art is covered below. What matters to the institution's origin is what the art required: it needed the \textit{true name}, it worked better with the quarry's leavings in hand, and it went wrong --- badly, memorably --- when the name was wrong. A trade with those requirements cannot run on rumor and a handshake. It needs the name verified, the grievance documented, the terms written, the payment held against delivery, and the whole instrument voided root and branch the moment an error surfaces --- and that instrument is the \textbf{writ}, and the institution that grew up around the writing of it is the Registry.

So the Registries are, in their bones, a documentation practice wrapped around a psychic art --- clerks and adjudicators building paper walls around something that hunts through dreams --- and the trade's foundational irony is that the paper came to matter as much as the art. A writ, properly drawn, is the closest thing the stateless world has to a warrant: proof that a named person, for a stated cause, within posted jurisdictions, has been lawfully made \textit{huntable}. The Registries guard that power with a strictness that borders on the liturgical, because they know exactly what they are for. They are the court of last resort. Last resorts that get careless become first resorts, and first resorts of this kind have another name, and the Registries' entire institutional culture is the determination never to earn it.

\medskip\hrule\medskip

\subsection{The Read}

The Bounty Hunter's art is the setting's other discipline of the mind, and the two traditions define each other by contrast. The Orders' Eye is trained on the great sea --- the shared unconscious, the dreaming that underlies all minds --- and its ethics forbid entering any one of them uninvited. The Hunter's art ignores the sea and follows \textbf{one wake through it}.

The tradition's own account, taught at every certification bench: a mind sheds. Continuously, helplessly, waking and sleeping, every person leaks self into the dreaming --- habits, hungers, the shape of their choices, the weather of their fears --- the way a body sheds warmth, scent, and footprints into a landscape. The Hunter does not enter the quarry's mind, and this distinction is the hinge of everything: the Hunter \textbf{reads the shed} --- casts for one specific wake in the drift of all that leaked selfhood, finds it, and follows. \textit{We don't open doors,} runs the benches' formula, polished by two centuries of saying it to suspicious monks and frightened towns; \textit{we read footprints.} The Orders' examiners tested the formula for eleven years before ruling, in the grudging judgment the two traditions have lived on since, that the shed self is leavings, not interior --- track is not trespass --- and the Closed Door stands unbreached. A minority of the Bell's masters have never accepted the ruling. The Hunters' benches keep the ruling's text framed on the wall, which is not the same as thinking the minority wrong.

What the Read requires is what the writ supplies. \textbf{The name, first and absolutely}: the true name is the thread by which one wake is found among millions, and a false name finds a false wake --- which is not failure but catastrophe, the Hunter converging with perfect confidence on the wrong soul --- and this is the fact beneath the trade's most famous law: \textit{the writ voids on error}. Not as courtesy. As safety interlock. \textbf{Relics, second}: the quarry's leavings in the physical world --- a possession long-carried, a page in their hand, above all their blood --- anchor and deepen the Read, and the writ's evidence annex, where the client's keepsakes are catalogued and sealed, is as much the Hunter's toolkit as the legal record.

What the Read gives, by depth --- and depth is bought with time, proximity, and relics: at the shallow end, \textbf{the bearing} --- direction and distance as a heat behind the eyes, the trade's compass. Deeper, \textbf{the habits}: the quarry's patterns arriving as instinct --- which road he takes, which lies he prefers, when he sleeps --- until the Hunter anticipates like an old partner. Deeper still, \textbf{the dreams}: the Hunter sleeps and walks the quarry's shed dreaming, and wakes knowing what the quarry fears is behind him, which is the trade's true edge, because a man's plans live one layer above his fears and are legible from below. And at the profession's rare full depth, \textbf{the closing}: in the final days of a long hunt, quarry and Hunter begin to share weather --- each dreaming the other, the pursuit becoming mutual and strange --- and the endgame of every deep Read is a meeting between two people who know each other with dreadful intimacy and have never spoken. Veteran Hunters are famous for the courtesy of that meeting. It is not affectation. By the end, arrest feels like keeping an appointment both parties are relieved to stop dreaming about.

The art's dangers are the mirror of its method. \textbf{Going over}: a Hunter too deep too long begins carrying the quarry home --- the tastes first, then the temper, then, in the tradition's disasters, the loyalties; the benches mandate surfacing intervals, partner-watch, and the retirement of any Hunter who has closed on a quarry and hesitated without cause, and the trade's Sundered-equivalent --- the Hunter who finished a hunt as someone else --- is its private ghost story and its genuine occupational disease. \textbf{The read-back}: a psychic quarry --- a monk, another Hunter, certain things that are not people --- can feel the Read, seize the thread, and follow it \textit{backward}, and the duel that results, fought entirely in shed dreaming across hundreds of miles, is the profession at its most dangerous and its practitioners at their most unwilling to discuss. And \textbf{the baffles}: the Read can be defeated --- by warded sleep, by a name lived-away-from long enough to thin, and, most completely, by the masks of the Nol, whose tradition was forged, ages before any Registry, against \textit{predators of the unseen world that hunt by familiarity} --- a description the Hunters' benches read, when Nol certification candidates first presented it, with the professional discomfort of men shown their own portrait in an older gallery. A masked quarry is hunted the hard way. Nol Hunters, conversely, hunt \textit{wearing} the older defense, and are prized for exactly the jobs where the read-back kills.

\medskip\hrule\medskip

\subsection{The Writ}

The writ is a physical instrument, and the frontier can read one at arm's length.

Heavy paper, registry-watermarked; the \textbf{name} in display hand across the head --- the true name, verified by the adjudicator's inquest, sworn to by the client on penalty of the voiding and its costs; the \textbf{cause}, stated plainly, because the Registries post no writ whose grievance they will not print; the \textbf{jurisdictions}, listed --- a writ runs only where posted, and reciprocity between registries (the Exchange of Seals) is what lets a Thirstgate writ be honored at Lastlight; the \textbf{terms} --- \textit{to answer} (brought to adjudication), \textit{to hold} (delivered to a named custody), or, in the writs the benches draw most reluctantly, \textit{dead or answering}, the trade's exact and chilling phrase; the \textbf{fee and escrow marks}, the client's payment held by the registry against delivery, so that no Hunter ever collects from the person with the grievance; and, sealed to the foot, the \textbf{evidence annex}: the relics. A writ is void on error, void past its term, void outside its posts, and void --- article older than the Exchange itself --- the instant the named person dies of any hand but lawful execution of the terms, because a writ is a license to \textit{find and answer}, never a subscription to a death.

Around the instrument, the institution's hard cases, unchanged in kind since the founding and refreshed in every generation:

\textbf{The House bounties.} The Houses bring the Registries their least legible grievances --- the runaway, the oath-breaker, the injuries that are real and not legally cognizable anywhere --- and the adjudicators' art is refusing the claim without insulting the House. The standing rule (\textit{no writ on a runaway who has broken no law}) is the benches' proudest line and most expensive one; the Houses' custom of hiring \textit{finders} instead --- locate, don't touch --- lives in the gap, and so does everything the gap implies.

\textbf{The rogue writs.} An Enclave's writ on a named Arcanist is the rarest paper in the system and the only kind the benches expedite without discussion. Every certified Hunter knows what it means that Returns has given up, and knows the standing bonus, and knows the question that will be asked, gently, at collection: \textit{was the book recovered?}

\textbf{The unsanctioned hunt.} Outside the writ system entirely: the private trackers, the House finders working past their brief, the vengeance trade --- everything the Registries exist to make unnecessary and cannot make extinct. The benches' posture is pragmatic hypocrisy, openly maintained: unsanctioned work is condemned, uninsured, unprotected --- and quietly monitored, because an unsanctioned hunter with the Read and no bench discipline is a going-over waiting for a road to happen on, and the registries' cleanup files on such cases are the strongest argument their certification system owns.

\textbf{Effacement.} The Registries' one punishment, reserved for those who corrupt the instrument itself --- the adjudicator who sells inquests, the Hunter who kills on a writ's margin, the registry that betrays the Exchange: the \textbf{voiding of the name}. Struck from every roll, unwritable on any writ, formally nameless --- civil death, in the trade the whole world trusts to say who may be hunted. It has been pronounced eleven times. And the eleventh is the trade's open wound, because effacement contains a flaw that was discovered exactly once, at the worst possible scale: \textit{a name that cannot be written cannot be Read.} When the Verge Registry was struck from the Exchange in 289 SR --- inquests sold wholesale, writs drawn on the innocent, the worst institutional corruption in the system's history --- its Provost was effaced with it, and the sentence made him the one man alive whom no writ can name and no Hunter's art can find. \textbf{The Effaced} has been working ever since: writ-forgery of impossible quality, inquest files that surface where they can do maximum harm, Hunters lured onto false names --- the system's own architecture, wielded by the only person standing wholly outside it. The standing arrangement among the registries for his case is unique, unwritten, and universally understood: he is hunted the old way, the hard way, by volunteers, off the books --- because the books are what he broke.

\medskip\hrule\medskip

\subsection{Benches and Boards}

A Registry is civic furniture: the hall with the \textbf{posting boards} (public writs on iron rings, jurisdiction flags above), the adjudicators' \textbf{bench} (inquests are heard in the open; the Registries' answer to every accusation of assassination-brokerage is a public gallery and always has been), the escrow vault, the evidence room, and the certification yard where candidates are examined --- in law first, in craft second, in the Read last and longest: depth discipline, surfacing drills, the partner protocols, and the examination the benches call \textbf{the cold name}, in which the candidate is given a writ whose name is subtly false and passes only by \textit{noticing} --- the trade certifying, before anything else, the reflex that keeps its power pointed at the right soul.

Certified Hunters carry the \textbf{seal-tag} --- registry seal, cert number, jurisdiction rings --- and the trade's tokens of standing are the rings: one per region of reciprocity, and an old Hunter's tag rings like a key-chain. Speech: a writ is \textbf{paper} (the trade shares the word with the Companies, and both know it); to begin a Read is to \textbf{take the name}; the bearing is \textbf{the itch}; a quarry gone masked or warded has \textbf{gone quiet}; a Hunter drifting too deep is \textbf{wearing the coat}, and a partner's flat \textit{``whose coat is that?''} is the trade's suicide-watch, answered honestly or not at all. The valediction, at postings and partings, is the oath's working line: \textit{``right name, whole road''} --- find the right one, bring them the whole way back.

\medskip\hrule\medskip

\subsection{The Registries}

Every city worth the name seats one; the Exchange of Seals binds them. These four span the trade.

\subsubsection{The Thirstgate Registry}

The model: the biggest boards, the deepest bench, the standing Lions account, and the Exchange's informal secretariat. Thirstgate's adjudicators staff half the Hov Convention's arbitration panels; its inquests set the evidentiary customs everyone else copies; and its First Adjudicator, \textbf{Provost Ana Vel}, has spent twenty years as the trade's institutional conscience --- author of the runaway rule's modern wording, keeper of the Effaced's off-book file, and the person the other registries call when a writ smells wrong. Her bench's culture in one detail: at Thirstgate, the voiding of a writ is announced with the same bell as a collection, rung the same number of times. Errors, Vel teaches, are the trade's true enemy, and the bell is so that no one ever learns to hear an error as a smaller sound.

\subsubsection{The Lastlight Registry}

The Verdant Belt fringe's board: smaller, harder country, and currently the most watched registry in the world, because Lastlight holds the Corvenwood writ --- Lady Ivress Corvara's record bounty on whatever is draining bodies along her tithe-routes --- and the inquest file that goes with it, which grows stranger by the season. Lastlight's adjudicators have verified what the House said from the first: the killings are fluent in Corvara practice --- routes, schedules, courtesies --- and fluent, the newest entries add, in things the House does not publish. The certified Hunters who have taken the name (the writ runs on a description and a working alias, the true name unknown --- the inquest's central problem, and the reason the Read keeps sliding off) report the same two findings: the quarry knows how Hunters hunt. And the trail, four times now, has bent \textit{east}, out of the Belt, toward the Dust Lanes, before going quiet.

\subsubsection{The Greywater Registry}

The delta mouth's bench: half writ-hall, half admiralty court, seated where House Ophara's salvage right, the Companies' cargo clauses, and the sea's own opinions require a permanent referee. Greywater's specialty is the arbitration trade --- its adjudicators are the Exchange's finest on questions of property, wreck, and jurisdiction, and its current docket holds the orichalcum case the whole coast is watching --- and its boards run to the trade's strangest paper: writs posted on ship-jumpers, cargo-thieves, and, in one standing instance the bench declines to discuss and has not voided, a writ drawn \textit{to answer}, true name verified by means the annex seals, on something the divers of the Serpent's Channel have only ever described by its hands.

\subsubsection{The Long Table at Dustline}

The frontier registry the frontier brags about: lean, exacting, and owner of the Exchange's best collection rate --- the Long Table's Hunters bring back the names nobody else can find, in country where the Unblinking's weather makes every other institution walk carefully, and the trade's saying is that Dustline paper is the hardest paper and the surest. The registry's public face is its First Adjudicator, a scrupulous Dust Lanes lawman of thirty years' standing. Its actual center is the \textbf{Night Bench}: the senior circle --- certain adjudicators, the registry's dozen finest Hunters --- that sits after dark, hears the cases that cannot wait for morning, and constitutes, though not one soul outside it knows the whole of this, the life's work of \textbf{Maren Corvara}.

Struck from the blood-book thirty-one years ago --- the only formal expulsion in House Corvara's records, for research the House will not name and has spent three decades not discussing --- Maren solved in exile the problem her House forbade her to solve at home: \textbf{the gift can be given.} Imperfectly. Her made vampires carry the thirst without the House's refinements --- faster than men, slower than Dynasts; night-eyed; hungrier, and hungrier \textit{crueler}, without the Corvenwood's bred restraint --- and, cast out of the only infrastructure ever built to feed such a thing ethically, they have no Tithe Book, no willing demesne, no smug healthy villages. What Maren built instead was the Long Table: a feeding architecture wearing a courthouse. The writ is the hunt is the meal --- \textit{dead or answering} paper preferentially taken, exsanguination unremarkable in bodies carried in from hard country; live deliveries tapped, carefully, en route --- and the gift is offered, selectively, down the years, to the registry's best: because Maren discovered the synergy that makes her Hunters the Exchange's finest and the trade's nightmare, though the trade does not know it yet. \textit{Tasted blood is the perfect relic.} A Hunter who has fed on the quarry holds the Read at full depth without effort, forever --- the bearing never cools, the dreams never blur, the name never thins --- and so the Night Bench does not track like other benches. It \textit{keeps} its names, the way the House that made its maker keeps a Tithe Book.

The registry's paper is genuinely clean --- Maren is her House's child in this if nothing else; the Long Table's inquests are immaculate, its escrow exact, its collection ethics formally beyond reproach --- and its secret is fraying at exactly one seam: appetite. The gift she gives is crueler than the one she was born to, some of her made are younger in their control than she believes, and four times now, on the Belt fringe two regions west, something with House fluency and no House restraint has fed sloppily along the Corvenwood tithe-routes and staged the leavings to point home --- at the House that cast her out. Lastlight's inquest file bends east. Lady Ivress's recalled reader, Solenne, has begun asking the Exchange for thirty years of Dustline collection records. And Maren Corvara, who has spent three decades building the one thing that lets her kind exist --- lawful, fed, and \textit{necessary} --- now confronts the founder's oldest arithmetic: everything she made is one sloppy feeding from a writ with her own true name at the head of it, and she, better than anyone alive, knows exactly how good the Hunters who would take that name are. She trained them.

\medskip\hrule\medskip

\subsection{The Registries Among the Factions}

\textbf{The Companies} (both kinds) meet the benches at the border of paper: the Hov Convention's panels, the bare feeding the boards, and the jurisdictional catechism every Captain and Hunter learns --- \textit{writs name persons, paper covers clients, compare documents before either draws.} The Jackal application has put three live writs at the center of the trade's biggest precedent question, and the benches' position is the institution in one line: the writs stand until answered; redemption is the Rolls' business; \textit{names} are ours.

\textbf{The Lions} keep the standing Thirstgate account and the old unease: the mainline values an institution that documents its violence; the Unblinking distrust an art that swims the dreaming, however footnoted the footprints ruling --- and the Long Table's flawless service in the Unblinking's own heartland is, for anyone who ever learns the whole of it, the setting's blackest joke.

\textbf{The Orders} hold the Read's license in trust, decennially re-examined, minority dissent unretired. Still Water's examiners and the certification benches have, over generations, become each other's most respected critics, and a Hunter drifting toward the coat is, quietly and often, sent to sit by still water --- the one referral both traditions make without paperwork.

\textbf{House Corvara} and the Registries share the oldest account on the boards (the undead paper) and now, unknowing, the newest wound: the House hunts the Shadow's vampires, defends the born gift's honor, and does not yet know that the thing wearing its practices in the Corvenwood was made --- and that the making is the research it would not discuss. When the Lastlight file and the Exchange records finally meet, the question of what House Corvara does about Maren's children will make the Talvecq petition look procedural.

\textbf{The Nol} occupy both sides of the art: the trade's most baffling quarry and its most sought certification candidates, and the benches' relationship with the mask tradition --- older than the Read's own name for itself --- is conducted with the care of a young discipline that has met its elder.

\textbf{The Enclaves, the Guilds, the Houses at large}: the specialty dockets --- rogue writs, mark-forgery paper, the finders' gap --- each covered in its chapter, all converging on the same boards.

\medskip\hrule\medskip

\subsection{Current Fault Lines}

\begin{itemize}
    \item \textbf{The Corvenwood Convergence.} Lastlight's trail bends east; Solenne Corvara-Mar has asked the Exchange for Dustline's records; the Night Bench's youngest made are getting hungrier and worse at it; and Maren Corvara is running out of clean exits at the pace of one staged body per season. Whichever institution assembles the picture first --- the House, the Exchange, the Lions --- inherits a crisis with three heads: a killer, a registry, and \textit{proof that the gift can be given}.
    \item \textbf{The Effaced, Active.} Forged writs of impossible quality have surfaced in three jurisdictions this year, each drawn on a person someone powerful wanted huntable --- the system's authority, counterfeited by the man the system unnamed. Vel's off-book file has begun recruiting.
    \item \textbf{The Quiet Trade.} Someone is selling Read-proofing --- warded sleep, name-thinning regimens, mask-work of non-Nol manufacture that the Nol deny and denounce --- to exactly the clientele the boards exist for. The benches' nightmare is not the baffles; it is the vendor's inventory list, which is, necessarily, a directory of everyone who expects to be hunted.
    \item \textbf{The Revenant Paper.} The Dust Lane revenant writs --- posted on the changed Talvecq after 259, uncollected for decades --- are up for their jurisdictional renewal, and Severin Talvecq has filed, through Ardenne counsel, the objection the benches have dreaded for years: that the writs name persons who may no longer exist as named, drawn on evidence sealed by Leo himself, and that the Registries are renewing paper on souls whose status is precisely the question his petition asks. The benches must rule on whether the names still \textit{hold} --- which is to say, on what the Cascade left --- years before anyone opens the seal that knows.
    \item \textbf{The Jackal Names.} Three live writs, one redemption application, and the Exchange's first formal collision with the Rolls: if the Convention admits the Jackals while the writs stand, the trade's two great documentation systems will have certified, about the same three men, opposite things.
\end{itemize}

\medskip\hrule\medskip

\subsection{The Registries in Play}

\textbf{Playing the Hunter.} The class is the setting's psychic rogue, and the chapter hands it three engines. The \textbf{Read} makes every hunt a relationship: the GM's quarry is not a location to find but a mind to converge with --- habits learned in play, dreams shared on bad nights, the closing courtesy at the end --- and the depth mechanics carry the class's built-in dilemma (deeper is faster, and deeper is the coat). The \textbf{writ} makes every job a legal instrument with edges: names, terms, jurisdictions, and the voiding, so that the classic rogue verbs --- infiltrate, shadow, ambush, extract --- happen inside paper that can tear. And the \textbf{bench} makes the Hunter a professional among professionals: certification, the partner protocols, the seal-tag's rings --- or none of it, for the unsanctioned variant, the wild Read on the far side of the trade's own boards, hunted a little by everyone including the benches, which is a complete campaign premise in itself.

\textbf{What the boards pay adventurers to do.} The writs themselves, first and always --- the boards are the setting's native job system, sorted by jurisdiction and legible at a glance --- and around them the trade's support economy:

\begin{itemize}
    \item Take plain paper: the answering-writs and holding-writs that are the trade's bread --- and learn, on the road, that the Read's targets are people, which the benches consider the most important thing the easy jobs teach.
    \item Serve an inquest: verify a name, run down a relic's provenance, depose witnesses three towns apart --- the adjudicators hire out the legwork that makes writs safe to write.
    \item Escort a delivery: a held quarry, a rites-sealed evidence annex, an escrow transfer --- the jobs where the party guards the system rather than works it.
    \item Partner a deep Read: a Hunter closing on a long name needs exactly what a party is --- eyes on the world while hers are in the wake, and someone certified to ask, at need, \textit{whose coat is that?}
    \item Hunt the quiet trade's vendor up the inventory list, jurisdiction by jurisdiction, before the list finishes becoming a customer ledger.
    \item Work the Corvenwood writ --- the biggest open paper in the world --- far enough east to earn the Long Table's professional hospitality, and be the party in the room when someone finally notices that Dustline's finest never seem to need the annex relics at all.
    \item Volunteer for Vel's file: the Effaced is hunted the old way, off the books, by people the system's architecture cannot betray because they are not written into it --- which describes an adventuring party better than anything else in this book.
    \item At the highest tiers: stand before the benches at the revenant-paper hearing, as evidence-bearers, witnesses, or the ones lately returned from the trusteeship lands --- and help the trade answer the question underneath its whole instrument: when the person is gone, what, exactly, still holds the name?
\end{itemize}

\textbf{Patrons.} \textit{Provost Ana Vel} --- clean paper, exact fees, and, for the twice-proven, the other file: her errands touch the Effaced, and she staffs them like a woman defusing something. \textit{An adjudicator of Greywater} --- the arbitration docket's investigations pay coastal rates and read like sea-stories, and the standing instance in the sealed annex is eventually going to need visiting. \textit{A senior Hunter of the Long Table} --- the finest field mentor the trade can offer a young party: generous, patient, encyclopedic, never hungry at dinner, and the campaign's slowest, best question is how long it takes the party to count the things wrong with that sentence.

\medskip\hrule\medskip
