% ============================================================
% INTER-FACTION RELATIONS — REBUILD (capstone chapter)
% ------------------------------------------------------------
% Supersedes inter-faction-relations.tex. Written to inherit the
% full rewritten canon: nine factions, the Timeline, and the
% ~30 live fault lines distributed across the faction chapters.
% Focus per author direction: HISTORY, CONFLICTS, TENSIONS.
%
% STRUCTURE:
%   1. The frame (pairwise, not systemic — kept from original)
%   2. The Sediment (shared history as the source of current
%      relations: six structuring events)
%   3. The Machinery of Peace (how disputes are actually
%      adjudicated — the gap the original left open)
%   4. The Tensions (pairings in five thematic clusters; all
%      previously-missing pairs covered)
%   5. The Matrix (9x9 quick reference)
%   6. Flashpoints (cross-faction crises live at campaign start)
%   7. The Deep Currents (GM-facing: the three braids no single
%      chapter owns — incl. the Waking Made, stated explicitly
%      here and ONLY here)
%   8. At the Table (GM guidance)
%
% No new canon proposed except: the jurisdiction rule that writs
% do not run past the markers (Registry paper ends where sovereign
% country begins), and the naming of the three Deep Currents.
% ============================================================

\section{Inter-Faction Relations}

\subsection{The Frame}

The factions relate pairwise, not systemically. This is the chapter's first rule and the setting's deep habit: there is no alliance axis, no two-bloc map, no great game with sides --- there are some forty standing relationships, each with its own history, temperature, and paperwork, and a faction that is another's indispensable partner in one matter is its patient adversary in the next, often through the same office, sometimes in the same afternoon. The stateless world produced this shape on purpose. Blocs are claims, and claims are answered; a web of specific bilateral understandings is the largest political structure the threshold has ever tolerated, and everyone who matters knows it, mostly without knowing they know it.

Two corollaries govern everything below. \textbf{Relations are regional}: the Enclave--Lions relationship is a working partnership in Thirstgate and a cold war in the Dust Lanes, and both descriptions are simply true, at the same time, a rail-week apart. And \textbf{relations are personal at the joints}: institutions hold positions, but the load is carried by individuals --- a liaison of twenty years, a Warden and a Rider who share a relay post, two factors at dinner --- and the standing rule of frontier politics is that the official relationship tells you what is possible, and the personal one tells you what will actually happen.

\medskip\hrule\medskip

\subsection{The Sediment}

Current relations are old events, still settling. Six of them carry most of the weight, and a reader who holds these six can derive the temperature of nearly every pairing below from first principles.

\textbf{The Unmapping} taught everyone the same lesson at the same time --- \textit{the Wild answers claims in proportion to their scale} --- and every institution in this book is, structurally, an answer to it: the Companies' commercial fiction, the Houses' small demesnes, the Guilds' land-without-territory, the Orders' claim of nothing, the network's whole vocation. This is the factions' deepest common ground and their least discussed: they are all survivors of the same verdict, shaped by the same fear, and the tension it generates is generational --- every institution's old hands remember why the walls are where they are, and every institution's young ambition leans on them.

\textbf{The Concord of Carriers} (1 SR) made the Companies, the Guilds, and the proto-Registries co-authors of the civil order --- dates, coin, contract, arbitration --- and the co-authorship is still the commercial web's emotional truth: these three factions quarrel like partners, not strangers, because they are. Everyone else joined a going concern, and the distinction shows: the Lions, Houses, Orders, Enclaves, and network all hold, in different accents, the reservation that civilization's operating system was written by its merchants, and the merchants hold, in one accent, the answer that nobody else showed up to the meeting.

\textbf{The Boundary Wars} (118--126, 244--251 SR) built the frontier's crisis architecture and its scars in one pour: the Accord of Operations (the fiction that was a peace term), the Incursion Pool, the Winter Concession --- and the precedent that when the Wild moves at scale, the only diplomatic channel civilization possesses is the network and the plains peoples, a dependence the settled factions have never enjoyed and never replaced. Meridian \& Norther's grave, the Rust Belt, and the never-discharged columns are the wars' unfinished business, and everyone's file on everyone else contains, somewhere, the question of how the other behaved in 249.

\textbf{Vellhame and the Kindling} (189, 211 SR) are one wound in two acts: the catastrophe that taught the world to fear the arcane, and the atrocity --- unattributed, unresolved, a century old this year --- that taught the Enclaves what the fear could do. Enclave--Lions relations everywhere are conducted on top of these two dates; the Library's records offer has just made the older one, briefly, negotiable; and the deepest tension the pair generates is not between the two factions but \textit{within} each --- the Lions' factions divided over what Vellhame licenses, the Enclaves' generations divided over what the Kindling forbids them to forgive.

\textbf{The Cascade} (259 SR) --- the fall of House Talvecq --- is the Houses' private terror made public policy: the proof that a gift can outrun its line, the reason the Concord of Seats refuses all study of the blood, the cause of the only seal in the Lions' archive, and the silent third party at every table where the Houses and the Enclaves sit. It is also the setting's most instructive case of inter-faction \textit{cooperation}: the cover story was agreed between the Concord and the Lions within the year, has held for five decades, and is currently held shut by two institutions against the sustained, guaranteed, entirely legitimate petition of one patient man --- which is the kind of arrangement this chapter exists to describe.

\textbf{The Night of Cut Ledgers} (308 SR) is the newest sediment and still warm: the first time in the reckoned centuries that a contemplative tradition intervened, physically, in the commercial order --- and the first time the commercial order discovered that its foundations are \textit{documents}, and that something in the world cuts documents. Four years on, the Orders' neutrality is questioned in rooms it was never questioned in, the Companies keep triplicate ledgers in separate towns, an unregistered bounty sits at every abbot's gate, and every faction has quietly updated the same internal memo: the monks were the fixed point, and the fixed point moved.

\medskip\hrule\medskip

\subsection{The Machinery of Peace}

The stateless world's disputes do not go unresolved; they go to \textit{instruments} --- specialized, bilateral, and jealously maintained --- and the machinery deserves its own accounting, because half the flashpoints below are attacks on it rather than through it.

\textbf{The Ardenne seal} is the apex instrument: enforceable agreement between parties who share no law, breach legible on a notary's skin, four generations unbroken. The seal is what makes the other machinery trustable --- Convention awards are sealed, Concord instruments are sealed, the Winter Concession is sealed --- and House Ardenne's neutrality is therefore the single point of shared dependence in the entire system, a fact the House carries with visible weight and everyone else prefers not to say aloud.

\textbf{The Hov Convention} arbitrates the world of paper: Company against Company, client against client, staffed by Registry adjudicators, enforced by the actuarial truth that fighting is dearer than losing. \textbf{The Exchange of Seals} does the same for names, binding the Registries into one jurisdiction of last resort. \textbf{The Concord of Seats}, \textbf{the Vellhame Convocation}, \textbf{the Table of Halls}, and \textbf{the Gathers} govern their own: recognition, protocol, marks, and ground --- each a peak body with no army, ruling by the one sanction the stateless world respects absolutely, which is expulsion from the web.

Notice what the machinery lacks: a keystone. Nothing sits above the instruments; they interlock without hierarchy, which is their strength (no keystone can be captured) and their live vulnerability (no keystone can defend the joints) --- and the current decade's signature development, visible from this chapter as from nowhere else, is that the joints are being tested deliberately for the first time: Argent Line sequencing the Convention's own escrow flows; Vault \& Coil posting bounty paper outside the Exchange; the Southreach Survey treating the oldest instrument of all --- the threshold itself --- as superstition with a margin. The machinery of peace was built to process disputes. It has never before had to survive being \textit{the} dispute.

\medskip\hrule\medskip

\subsection{The Tensions}

The forty-odd pairings, clustered by the questions that organize them. (One-line statuses for every pair appear in the matrix that follows.)

\subsubsection{The Lions and the Powers}

The Lions relate to every supernatural tradition through one question --- \textit{what is it, and what does it owe?} --- and each tradition has drawn a different answer from the organization's internal argument. \textbf{The Enclaves} get both answers at once, sorted by region: a century of demonstrated coexistence where the mainline holds, careful distance where the Unblinking are ascendant, the Kindling underneath everything, and this year, the Library's offer --- records for records --- arriving in the exact season the succession makes every archive a weapon. \textbf{The Houses} get the origin doctrine: Covenant lines received, Bargain lines suspected, conduct-over-origin holding by one Banneret's health --- and the Talvecq petition sitting on the desk where the two factions' oldest secret and newest crisis are the same document. \textbf{The Orders} get the answer the Lions do not have: a power that is neither divine, arcane, nor blood fits no doctrine, threatens no doctrine, and answers to a discipline even the Unblinking respect --- warm at the Threshold, wary at the Bell, unresolved at the Second Reading, whose interventions have finally forced the question the abstraction always deferred. And \textbf{the made soldiers} get the strain: the Lions sort the Mercenary trade by its stock, the Second Muster's leased dead carry the mainline's tolerance at maximum load, and the liaison audit that will find the Ostrey gap is already scheduled.

\subsubsection{The Houses and the Students of the Blood}

Everyone wants to read the Houses, and the Houses' one unanimous position is \textit{no}. \textbf{The Enclaves'} research appetite is genuine, respectful, and refused --- after the Cascade, the Concord's doctrine on the study of gifts is dread, not principle --- and the Vehk petition is the live case both signatories know is not really about the Vehk. \textbf{The Guilds} meet the Houses in the body: the Corvara--Red Thread arrangement, the Sawbones' suspicion that the blood-books are withheld case libraries, the Tinkerers' complicated awe of Cold Anvil --- the system's most sophisticated managed friction, currently unmanaged at exactly one point (the ethics query the Meliane affair left behind in the Salt Reach halls). \textbf{The Registries} hold the demesne-stone protocol and the runaway problem --- the writ that stops at the stone, the runaway who broke no law, the unsanctioned hunts in the gap --- and, unknown to both institutions, the Houses' worst secret is currently \textit{operating a Registry}: the Long Table's Night Bench is the Corvara research made flesh, and the day the Lastlight file meets the Exchange records, the Houses--Registries relationship acquires a crisis for which no protocol exists. \textbf{The Wardens} and the Houses barely touch except where they grip: the boundary demesnes, and the Ferrant grief --- the House the anathema bars absolutely, the courtesy channel the Wild pretends not to notice, and now the herd question traveling toward the Patient Stone, the largest favor the network has ever been asked to carry for iron.

\subsubsection{The Commercial Web}

The Concord's three co-authors, quarreling like the partners they are. \textbf{Companies--Guilds} is dependence weaponized: the register cannot run without licenses, marks, and Hearts; the halls cannot be starved without the Freeze-style plumbing attacks that Argent Line has now invented; and between the dusted strike shelf and the sequenced remittances, the oldest partnership in the world is conducting its first true test of strength, politely, through escrow. \textbf{Companies--Mercenaries} is the paper, and Redwater has put the whole enforcement portfolio before the Convention: \textit{what does a client buy?} --- the question three centuries of profitable ambiguity have deferred, now scheduled. \textbf{Companies--Registries} is the tidy pairing (the Greywater docket, the writ-work, the arbitration staffing) with one live splinter: V\&C's unregistered bounty on the Second Reading monks, which the Exchange has formally noted, and which every adjudicator understands as the register experimenting with what happens when it prices names outside the system that exists to keep names priced. \textbf{Companies--Lions} is moral pressure against funding tangles: the Riders at the pickets, the vim doctrine arriving at the inventory, and the works-towns filling with people the Companies do not owe anything to and the Lions insist on owing everything to, which is not a dispute so much as two theologies of the same census.

\subsubsection{The Boundary Traditions}

\textbf{The Wardens} price everyone's frontier and belong to no one's interior, and their pairings all carry the same asymmetry: indispensable, trusted, and never entirely \textit{ours}. With \textbf{the Companies}: the assessments, the integrity clause, the weariness --- and now the Southreach Survey, which has produced the network's first total refusal of contract in its recorded history, a fact the register's older boards read correctly and its youngest refuses to. With \textbf{the Lions}: the necessary marriage --- relay lines for weight, guides for mandate --- managed Warden by Warden, and about to be stress-tested by the Rust Belt question, where the Lions' hardest voice is demanding action on ground the network has just classified \textit{not ours, not theirs}. With \textbf{the Enclaves}: one deep channel (Northwatch) and a broad shallow one (the informant webs overlap in the field), two temperamentally opposite traditions that cooperate better than either's doctrine predicts. With \textbf{the Guilds}: the grow-yard watch, lately promoted from courtesy to necessity by thirty paces of fence line at the Overdrawn Yard. And with \textbf{the Orders}: the kindred quiet --- the two want-nothing traditions, the tolerance observation, the bell-ropes left where a Warden can reach --- the setting's most functional relationship, maintained by the shared understanding that formalizing it would be the first claim either had ever made.

\subsubsection{The Two Minds}

The Orders and the Registries hold the setting's disciplines of the mind, and their pairing is the system's finest piece of jurisprudence: the footprints ruling --- track is not trespass, the shed is not the interior --- eleven years in the testing, decennially re-examined, minority dissent unretired, and both traditions' examiners grown into each other's most respected critics. The tension it manages is permanent and honest: the benches' whole trade lives one doctrinal revision from prohibition, the Bell's masters have never accepted the ruling, and the working peace between the world's mind-healers and the world's mind-hunters is renewed, in practice, one referral at a time --- the Hunter drifting toward the coat, sent to sit by still water, no paperwork, the system's quietest joint bearing its most delicate load. The \textbf{Orders--Enclaves} pairing completes the triangle: opposite answers to the same terror (power that must be carried), mutual regard permanently edged --- the Slash Space dispute, the unrequited research hunger, and the once-a-generation cruelty about the gate and the eruption --- and underneath the edge, the field cooperation of frontier professionals who have both buried colleagues the other tradition's doctrine could not save.

\medskip\hrule\medskip

\subsection{The Matrix}

One-phrase statuses; read row-meets-column; regional variation applies to everything.

\begin{center}
\small
\begin{tabular}{l|llllllll}
 & \textbf{HOU} & \textbf{ENC} & \textbf{ORD} & \textbf{GLD} & \textbf{MER} & \textbf{TRA} & \textbf{REG} & \textbf{WAR} \\
\hline
\textbf{LIO} & origin-read & wounded/working & unplaced & vim-strained & sorted by stock & moral pressure & wary account & necessary marriage \\
\textbf{HOU} & --- & refused study & one endorsement & managed friction & seals \& clients & fixed terrain & stone \& runaway & grief \& gratitude \\
\textbf{ENC} & & --- & edged regard & polite fiction & ward contracts & useful doctrine & rogue writs & one deep channel \\
\textbf{ORD} & & & --- & gate \& ledger & bounty standoff & ruptured & footprints ruling & kindred quiet \\
\textbf{GLD} & & & & --- & licensing hand & the Freeze & clerks' comfort & grow-yard watch \\
\textbf{MER} & & & & & --- & Redwater question & adjacent trades & priced by walks \\
\textbf{TRA} & & & & & & --- & docket \& splinter & the refusal \\
\textbf{REG} & & & & & & & --- & ends at the markers \\
\end{tabular}
\end{center}

(The last cell states the one jurisdictional rule this book has not yet written down: \textbf{writs do not run past the markers.} Registry paper ends where sovereign country begins --- a limit the Exchange has never contested, the network has never needed to enforce, and every Hunter learns the day they first watch a quarry walk, deliberately, past the \textit{do not} glyph, and stop being paper's problem.)

\medskip\hrule\medskip

\subsection{Flashpoints}

The cross-faction crises live at campaign start, each carrying its full write-up in the chapters cited and summarized here by what it \textit{tests}.

\textbf{The Succession at Thirstgate} tests everything, which is why it leads. Vairo failing, Fadrick positioned, the mainline candidateless --- and half the flashpoints below resolve differently under each outcome: the Talvecq petition lives or dies with the Banneret; the Library offer is grasped or spurned; the origin doctrine holds or hardens; the eastern funding ultimatum becomes precedent or footnote. The Lions' internal argument is the setting's weather, and the weather is turning.

\textbf{Redwater} tests the most institutions at once --- the setting's showcase pileup: eleven dead workers (Guild), a strike (the towns' question), a law-enforcement contract read very slowly (Mercenary doctrine), a Rider at the picket (Lions), monks in the hills (the Second Reading), and a client demanding the Convention define, in general terms, what enforcement paper buys (Companies against everyone's ambiguity). Whatever is ruled at Redwater is ruled for the world.

\textbf{The Freeze} tests the machinery itself: Argent's sequencing has moved from Guild dues to Convention escrow --- from pressuring a rival to leaning on the plumbing of peace --- and the response, when it comes, will define whether the instruments defend their joints jointly or discover, in public, that nothing requires them to.

\textbf{The Southreach Survey} tests the oldest wall: comprehensive cartography, launching in spring, over the network's first total refusal --- and the deeper test is discursive, because stopping it requires some institution to say, in public, what everyone believes and the fiction has made unsayable. The Survey is either about to be very expensively wrong, or the threshold really has moved, and no living institution knows which answer it is more afraid of.

\textbf{The Corvenwood Convergence} tests secrecy against jurisdiction: a killer fluent in House practice, a trail bending east, an Exchange records request en route to Dustline --- and, waiting at the end of the paper chase, proof that the gift can be given, which detonates the Transfusion Question, the Corvara's standing, the Lions' conduct doctrine, and a superbly run Registry, in whichever order the discovering institution chooses.

\textbf{The Library Offer} tests whether a century-old wound can be closed on purpose: records for records, wound for wound, timed --- the Library does nothing without three reasons --- to the exact season the archives are weapons. If the exchange happens, the Kindling gets an answer. Nobody has established that both institutions can survive one.

\textbf{The Vehk Coalition} tests the Houses' one unanimous position: a respectable petition made into a channel for every southern appetite at once, a House hiring outsiders to find the coordinator, and the Concord's dread-doctrine holding against exactly the alliance it always predicted.

\textbf{The Jackal Application} tests whether the webs have exits: restitution against live writs, the Rolls against the Exchange, and the certainty that whatever is decided about three un-withdrawn names becomes the stateless world's first formal doctrine of redemption.

\medskip\hrule\medskip

\subsection{The Deep Currents}

Three patterns run beneath the flashpoints, cross every border, and belong to no chapter --- which is to say, they belong to this one. They are written here for the table's eyes; no institution in the setting has assembled any of them entire.

\textbf{The Waking Made.} In one year: a creche colonel stands un-nominated for a charter; a leased dead trooper says his daughter's name; a grown line declines a lawful recall and a town takes its side; eleven frames at Cold Anvil turn as one to face the mountains; and Antler-Who-Counts opens a new column whose total exceeds anything anyone can enumerate. Five incidents, four kinds of made thing, zero people positioned to connect them without losing everything by the connection --- the Muster's theology, the March's precedent, the Green Chain's licenses, the Ferrant's origin, the trade's whole stock economy. Something is arriving in the made things, or waking in them, or being \textit{paid in} --- the Overdrawn Yard's Warden chose her words --- and the setting's institutions are structurally incapable of seeing it first, which is a job description, and the job is the party's.

\textbf{The Thinning.} The Glass Plains trend line has not flattened; the Wild's own courts are withdrawing from it --- the neighbors expect to be alive for whatever it ends in, and are moving; the vim question ties the whole energy economy to a boundary of the Heavens; and beneath everything, oldest of all, the scholars' unpayable line item: a bargain with the Wyrd, price forgotten, \textit{not the same as never coming due}. The setting's second current is simply this: the boundaries are becoming load-bearing questions at the same time, from three directions, and the institutions that watch them --- the Vehk, the Lions, the Convocation, the network --- have each noticed their own piece and filed it under their own dread.

\textbf{The Testing of the Web.} The Freeze, the private bounty, the Survey, the unanswerable Convention question --- read separately, four commercial overreaches; read together, the first generation since the Concord to probe whether the stateless order's instruments are laws or merely habits. The old hands built the web knowing why. The web has outlived most of them. And the setting's third current is the quiet race between the young powers discovering that the walls are unguarded and the old ones remembering, institution by institution, what the walls were for --- a race whose finish line is either a renewed order or the discovery, at scale, of what the Wild's patience has actually been waiting out.

\medskip\hrule\medskip

\subsection{At the Table}

Faction politics is not a subsystem; it is the terrain. Three notes for running it.

\textbf{Every job has a second client.} The chapters' hooks are written pairwise on purpose: the Guild contract crosses a Company's interest, the House commission crosses a Registry's writ, the Lions' errand crosses the network's ground --- and the reliable engine of faction play is not choosing sides but discovering, mid-job, that the job \textit{has} sides. Let the party find the second client at the worst useful moment.

\textbf{Fault lines resolve, and resolution is content.} The flashpoints above are load-bearing but not load-locked: Redwater will be ruled, the succession will be settled, the Survey will launch or burn --- and each resolution should visibly re-price the matrix. A world where the party watches the Freeze break the Table, or the petition open the seal, is a world that demonstrably moves, which is worth more than any single adventure the fault line could have hosted unresolved.

\textbf{Neutrality is also a position.} A party that ignores faction politics is implicitly asserting that personal relationships supersede institutional ones --- which is a meaningful stance in this setting, held by identifiable traditions (the Chosen, the network, the gate), respected by some institutions and read as available by others. The factions will not leave an effective party alone; the party's refusal to be claimed is, itself, the beginning of its reputation --- and, as the closing note of the previous chapter observes, the beginning of something else too. Every institution in this book was small once. The setting's history offers no examples of that stopping where it started.

\medskip\hrule\medskip
