% ============================================================
% LANDED GUILDS — REWRITE (superscience revision)
% ------------------------------------------------------------
% AUTHOR DIRECTION IMPLEMENTED:
%   - Guilds are artisans of ALL sorts (broad federation, mundane
%     crafts included), holding strategic neutrality WHERE THEY CAN
%     (neutrality as strategy, not sacrament — the bends are the
%     politics).
%   - The differentiator is SUPERSCIENCE: half-magic, half-science
%     arts with enough procedure and reason to be studied
%     scientifically, though full understanding eludes scholars.
%     Named arts: alchemy, spagyrics, energetics (+ harmonics,
%     somatics as minor arts).
%   - Tinkerer and Sawbones come from DIFFERENT guilds with
%     different specialties (many-to-many mapping; spagyrics
%     deliberately feeds both).
% CANON DECISIONS PROPOSED (all revisable):
%   - "Spyagric frames" read as SPAGYRIC frames: the living
%     machines are grown, not built — the Green Chain's art. Welds
%     to Ferrant/Cold Anvil and Vault & Coil.
%   - Epistemology: "the Procedure is the truth" — validated
%     replication without mechanism. The case libraries = archives
%     of validated procedure. In-world heterodoxy: the Whyseekers
%     (mechanism-chasers, mildly disreputable).
%   - Cosmological seam (offered as in-world speculation, not
%     stated fact): each great art rides a boundary — alchemy on
%     the Wild's rules of combination, energetics on the vim
%     question, spagyrics on the Realm of Wood.
%   - Named guilds: the Crucible (alchemy; orichalcum refining
%     licenses), the Green Chain (spagyrics), the Coilwrights
%     (energetics), the Red Thread (chirurgeons), plus the Assay
%     (certification body) and the mundane base.
%   - Federation: the Table of Halls. Ranks: apprentice ->
%     journeyman (the Walk) -> master (masterpiece) -> grandmaster.
%   - Historical breach: the Harrow Hall Judgment (248 SR) — the
%     one full expulsion; source of the Neutrality Protocols.
%   - Enforcer craft from the old draft is retired as a
%     class-bearing guild; hall security is a service trade.
%   - Kept from notable-factions: Grandmaster Korvo Vance.
%   - Cross-refs: timeline (Concord of Carriers co-signed by
%     proto-Guilds; 248 SR added), Lions (vim doctrine), Enclaves
%     (the polite fiction), Houses (Corvara training, Ferrant
%     hands), Orders (Cut Ledgers aftermath), regions, premise doc
%     (Hearts, ebbs, storage acid, biollurgy).
% ============================================================

\section{The Landed Guilds}

\subsection{Origins}

When the nations fell, the libraries burned, the mints closed, and the roads forgot where they went --- and the recipes survived.

They survived because they were not kept in libraries. They were kept in hands: the tempering sequence in the smith's arm, the tincture ratios in the apothecary's daybook, the nine-day patience of the tanner's pits, carried through the Silent Years by the people who could not stop knowing them. The craftsfolk of the dead nations discovered, in the worst generations the world has recorded, the two facts their descendants' federation is built on. First: that knowledge which feeds, heals, arms, and warms is the one property no collapse can confiscate. Second: that the individual holder of such knowledge is not powerful but \textit{portable} --- valuable to every armed band and safe with none of them --- and that the only protection for people whose wealth lives in their hands is other hands. The craft associations of the Silent Years were survival compacts before they were anything else: shared caches, shared training so no recipe died with its holder, shared retribution so no holder died cheaply.

By the time the Companies and the craft associations met to sign the Concord of Carriers, the associations were already what the Concord's text calls them --- \textit{the Guilds united} --- and the centuries since have added scale without changing the skeleton. The Guilds bought their halls outright, in every town worth a hall, which is the ``Landed'' in the name: property without territory, freeholds under the threshold, the largest holdings in the world that make no claim the Wild has ever bothered to answer. They wrote the certification systems that make a stranger's craft trustable three regions from home. And they held to the discovery that made a federation out of a survival compact: that the coopers and the masons and the printers and the alchemists are stronger as one Table than as forty trades --- because a boycott by the strange arts alone is an inconvenience, and a boycott by \textit{everyone who makes anything} is a siege.

That breadth is the first thing to understand about the Guilds. The federation is artisans of all sorts: the mundane base --- wrights, founders, weavers, millers, glassmakers, the honest bulk of the membership --- and, rising out of that base and crowning it, the arts that make the Guilds a faction rather than a trade fair. The world calls those arts by an old, half-admiring, half-uneasy word.

\medskip\hrule\medskip

\subsection{The Procedures}

Superscience is craft that works for reasons that will not entirely hold still.

It is not magic. It erupts in no one; it accumulates in no one; it answers to no bloodline, no cultivation, and no bargain. It is procedure: written, taught, replicated, measured --- \textit{if the mash is held at the third heat for the span of the long bell, the yield is constant; we have run it four thousand times} --- and it is science in every respect but the one that keeps scholars awake, which is that the full \textit{why} recedes at exactly the pace understanding approaches. Every great art has its scandalous clauses: the step that should be decorative and is load-bearing, the ratio that works at 3:7 and fails at 6:14, the dawn requirement that three generations of rationalists have died trying to delete. The Guild position on all of this is the position of people whose members handle the results at arm's length daily, and it is carved over the door of every case library in the federation: \textbf{the Procedure is the truth.} What replicates, is. Why it is can wait.

The case libraries are the federation's soul: archives not of theory but of \textit{validated procedure} --- every recipe with its provenance, its replication count, its failure modes, and its injuries, entered in the unsparing format the Guilds developed for the purpose and treat with a reverence the Enclaves reserve for their books. A procedure enters the libraries only through the Assay's replication protocols; a procedure leaves only by being superseded; and the theft or corruption of a case volume is, in Guild law, poisoning --- because that is, downstream, exactly what it is.

The great arts, by the Table's own reckoning:

\textbf{Alchemy} --- the transformation of matter: acids and alloys, solvents and salts, the refining arts, and the crown licenses of the trade, the orichalcum procedures, by which raw strange metal becomes the batteries of civilization. Alchemy's scandal is that its combinations follow \textit{rules} --- reliable, learnable, and unlike any chemistry the rationalists can derive from first principles, as if the discipline were transcribing someone else's grammar. The Guild's quiet heterodox note that the Wild is described, in the oldest cosmologies, as \textit{the rules of the combinations} is not doctrine. It is also not refuted.

\textbf{Spagyrics} --- the vital art: growth directed, life grafted, the green procedures. Spagyrics heals (the tincture and preparation trades that stock every Sawbones bag), feeds (the hardy strains that let towns eat behind walls), and, at the summit of the art, \textit{grows the frames}: the biollurgical chassis --- spagyric frames, in the trade's own speech --- the living machines that haul and plow and carry, bred in lines, gentled like stock, grown around bone and bio-metal in the vat-yards of the Green Chain. Spagyrics' scandal is generative: the art coaxes from soil and water a vigor that soil and water do not contain, drawing --- the heterodox note again --- on whatever underwrites growth itself, and the Wardens, who know what else draws on that, keep an eye on grow-yards sited too near the wild country, with a courtesy that fools no one.

\textbf{Energetics} --- the art of vim: the charging and keeping of power, storage acids and ebb-accounting, the jolt-lines that light the great halls, and the masterwork of the entire civilization, the \textbf{Constructive Heart} --- the engine-organ that moves the rails and beats, the Coilwrights like to say, under everything the frontier calls progress. Energetics' scandal is the loudest, because the Lions have made it doctrine-adjacent: if vim is truly a domesticated echo of the boundary between sky and Heaven, then every Heart is a small standing theological event, and the Coilwrights are either engineers or unlicensed clergy depending on which chapter house is asked. The Coilwrights' formal position is that they charge by the ebb either way.

Below the great three, the minor arts: \textbf{harmonics}, the resonance procedures --- vibration-forging, tone-testing, the bell-founders' strange precision, an art the Uln cold-smiths of the glacier cities practice at a refinement the lowland halls admit they license rather than match; and \textbf{somatics}, the chirurgeons' superscience --- the procedures of flesh, graft, and recovery that begin where honest anatomy ends and that the Red Thread documents with the arm's-length rigor of people who know exactly which volumes the Enclaves and the Houses would each pay fortunes to read.

And through all of it, the heterodoxy: \textbf{the Whyseekers} --- the mechanism-chasers, the members who cannot leave the \textit{why} alone. Every hall has a few; every grandmaster was warned about them as an apprentice; and the federation's attitude is the exasperated tolerance of an institution that knows its case libraries were all, once, some Whyseeker's disreputable afternoon. The standing joke is that a Whyseeker is a scholar the Assay hasn't caught yet. The standing truth is that the Guilds' deepest fear is not that the Whyseekers will fail, but that one of them, someday, will succeed --- and the why, once had, will turn out to be something the Procedures were kinder as.

\medskip\hrule\medskip

\subsection{Structure}

The federation is guilds all the way down, and the map of them is the map of the classes the world meets.

A \textbf{guild} is a craft: chartered, self-governing in its art, keeper of its own case volumes and its own masters' bench. The mundane guilds are the base of the Table and its ballast. The great-art guilds are fewer, richer, and carry the federation's weight in the world:

\textbf{The Worshipful Order of Alchemists} --- \textit{the Crucible} --- holds the matter arts and the orichalcum refining licenses, which makes it, quietly, a chokepoint of the entire energy economy: Vault \& Coil's conversion floors run on Crucible-certified refiners or they do not legally run. \textbf{The Green Chain} holds spagyrics entire, from the village tincture-bench to the great vat-yards where the frame lines are grown. \textbf{The Coilwrights} hold energetics: the Hearts, the storage acids, the jolt-lines --- and, therefore, the hand on civilization's pulse that gives the federation its ultimate argument (see below). \textbf{The Red Thread} --- the Chirurgeons' United Guild --- holds somatics and the medical case libraries, trains the world's Sawbones benches, and maintains with House Corvara the standing training arrangement both parties profit from and neither entirely likes.

The classes map across the guilds, not onto them. A \textbf{Tinkerer} may be Crucible-trained (a matter-and-mechanism artificer), Coilwright-trained (a Heart-and-charge engineer), or Green Chain--trained (a frame-wright, half mechanic and half drover) --- three educations, three temperaments, one word the frontier uses for all of them. A \textbf{Sawbones} may carry the Red Thread's surgical formation, the Green Chain's preparatory one, or the Crucible's toxicological one, and a good frontier practice usually shows two of the three in one battered bag. The guilds compete for the promising apprentice with a politeness that stops precisely at the hall door.

Rank is the same ladder everywhere, because the Assay makes it so. An \textbf{apprentice} is bound to a master and a hall --- fed, taught, worked, and entered in the rolls. A \textbf{journeyman} has passed the craft examination and taken \textbf{the Walk}: the wander-years, hall to hall and region to region, working under strange masters, carrying the little iron-bound \textit{walk-book} that collects a stamp and a judgment at every bench --- the federation's way of ensuring that no hall's craft closes in on itself, and, not incidentally, the finest adventurer's backstory the setting hands out for free. A \textbf{master} has presented the masterpiece --- examined, by unbreakable custom, by masters \textit{from another city}, traveling under escort for the purpose, so that no hall certifies its own --- and a \textbf{grandmaster} holds a hall and its seat at the \textbf{Table of Halls}, the federation's council, where the three hierarchies the Guilds actually run on meet: the craft hierarchy, which is real; the administrative hierarchy, which is real; and the political hierarchy, which does not officially exist, and which is where everything is decided. The acknowledged master of that third, invisible ladder is \textbf{Grandmaster Korvo Vance} of the Thirstgate hall --- a cooper by craft, a fact he deploys like a knife: the man who speaks for the strange arts to Companies and Lions alike holds no strange art at all, and can therefore say, with perfect truth, that he has no side even within his own federation.

The \textbf{Assay} stands apart from every guild and above none of them, which is the trick of it: the certification body --- the traveling examiners, the replication protocols, the mark that makes a stranger's Heart trustable and a stranger's tincture drinkable across three regions. The Assay's mark is the federation's true currency, forgery of it is the crime the Guilds pursue the way the Enclaves pursue books, and an Assay examiner on the road --- with the case volumes, the test-kit, and the authority to void a mark --- is one of the most consequential and most robbable figures in the world, which is why examiners travel escorted and why the escort contracts are a steady staple of the adventuring trade.

\medskip\hrule\medskip

\subsection{The Neutrality}

The Guilds are neutral where they can be, and the second half of the sentence is the doctrine.

The reasoning is structural, taught to apprentices as arithmetic: the Guilds sell to everyone, so the Guilds belong to no one; the moment a hall arms one Company against another, or one faction against another, every other client re-prices every Guild contract as a potential weapon --- and the federation's whole value, the thing that lets a Guild mark cross borders no state exists to guarantee, dies not by battle but by adjustment. Neutrality is therefore run as \textit{procedure}, exactly like the crafts: standing rules on dual-supply, escrow of disputed orders, the sealed-bid customs, the recusal ladders --- a case library of impartiality, validated by replication, its failure modes documented.

Documented, because it failed. In 248 SR, in the desperate middle years of the Second Boundary War, the Harrow hall in the north --- a Coilwright house of old standing --- ran munitions-grade energetics, exclusively and secretly, to one Company's private war against another while both burned Guild-marked freight. The federation's response, once the ledgers surfaced, remains the harshest act in its history: the \textbf{Harrow Hall Judgment} --- the hall expelled entire, its marks voided retroactively (a measure whose collateral cruelty the Table still argues about), its name struck from the rolls and retired from use. The Judgment is why the Neutrality Protocols exist in their current form, why apprentices learn the Harrow ledgers as a set text, and why the federation's answer to \textit{would you ever take a side} is not \textit{never} but the harder, truer thing: \textit{we did, once, and we know exactly what it cost, and we have written down the price where every member can read it.}

Where they can, then. The bends are real and the Table manages them in daylight where possible: the Guilds provisioned the Winter Concession talks (feeding both delegations is neutrality's finest hour); Guild halls treat the wounded of every side of everything, always, a rule with no exceptions clause at all; and when the Lions' mandate collides with a client's interest, the halls have a recusal custom so elaborate it constitutes taking a side very slowly. The one pressure the Protocols never anticipated is the current one --- because it attacks not the Guilds' products but their \textit{plumbing}, and it is covered below, under the faults.

And beneath the neutrality, never invoked and never forgotten, the argument of last resort: \textbf{the strike}. The Coilwrights alone could stop the rails in a week. The federation entire could stop \textit{everything}. The Table has authorized a general strike twice in three centuries, both times against attempts to seize halls outright, both times for under a month, both times conclusively --- and the institutional memory of those months is the true guarantor of every Guild charter in the world. The Guilds do not threaten. They maintain, in every hall, a plainly labeled shelf where the strike protocols sit, dusted weekly, in view of visitors. Grandmaster Vance calls it the federation's most productive bookshelf, on the grounds that no volume on it has been opened in eighty years.

\medskip\hrule\medskip

\subsection{Signs and Rites}

A Guildhall declares itself in oak, iron, and smell: scorched flux and green mash, hot acid's sting and the beeswax of the record rooms, under ceilings hung with the \textbf{masterpieces} --- every hall displays its masters' examination works, generations deep, and reading a hall's ceiling is reading its history. The \textbf{marks} are everywhere and legally sacred: the guild's device, the maker's device, the Assay's counter-stamp --- three marks make a lawful work, and frontier buyers who can read nothing else can read a mark-triangle at a glance, which is the point of it.

The rites are the ladder's: the \textbf{binding} of an apprentice (name entered, bread shared, the hall's oldest tool touched --- every hall keeps one, black with generations of hands); the \textbf{sending} of a journeyman onto the Walk, given the walk-book and the federation's blessing in its eternal form --- \textit{``learn what we don't know''}; and the \textbf{presentation} of the masterpiece before the traveled examiners, the one day the craft hierarchy outranks everything, when grandmasters stand and a journeyman sits. The dead of a hall are recorded in the case-library format, injuries and all, because the Guilds honor their dead the way they honor everything: by making the record useful. A member killed by a procedure has the procedure amended in their name. There are recipes in the libraries a century safer than they were, each carrying, in the provenance line, a name and the words \textit{paid for this}.

Speech: work is \textbf{marked} or \textbf{unmarked}, and the second word does the work of \textit{counterfeit}, \textit{dangerous}, and \textit{beneath discussion} at once; a procedure's unexplained load-bearing step is its \textbf{dawn clause}; a member flirting with mechanism is \textbf{asking why} (``he's been asking why again''); and the federation's all-purpose valediction, said at sendings, partings, and the close of the Table, is the first line of the Neutrality Protocols, which has escaped into the language: \textit{``sell to all, sworn to none.''}

\medskip\hrule\medskip

\subsection{The Guilds Among the Factions}

\textbf{The Companies} are the great client and the great pressure: the rails run on Coilwright Hearts, the conversion floors on Crucible licenses, the freight yards on Green Chain frames --- and the Companies, who resent every dependence they cannot buy, probe the federation's edges constantly: hall-trained workers hired away, parallel ``works schools'' founded and quietly starved of case-library access, and now the Argent Line maneuver (below), which is the first probe aimed at the plumbing rather than the product.

\textbf{The Lions} and the Guilds coexist on ground that shifted when the vim doctrine entered the Lions' internal argument. The mainline treats Guild works as morally inert craft; the Unblinking treat the Hearts as a theological question with a manufacturer; and the Coilwrights, caught between, have adopted the Table's oldest posture --- procedural, courteous, and armored in usefulness: the chapter houses, it is noted at need, are lit by jolt-line like everything else.

\textbf{The Enclaves} and the Guilds maintain the polite fiction --- that arcane craft and the Procedures are unrelated disciplines --- for excellent institutional reasons on both sides, while the working relationship underneath it thrives: containment engineering is Guild work to Enclave specification, eruption trauma is a shared Red Thread literature, and the Whyseekers and the Many Wells researchers drink together at every crossroads town in the registry, comparing scandalous clauses, each certain the other's discipline holds their missing piece.

\textbf{The Houses} meet the Guilds in the flesh and the vat: the Corvara--Red Thread training arrangement; the Green Chain's professional awe of the Cold Anvil works, where House Ferrant shapes by hand what the vat-yards grow by procedure; and the standing Sawbones suspicion, never voiced above a certain rank, that the blood-books of the Concord are the greatest uncatalogued case libraries in existence.

\textbf{The Orders} intersect the Guilds mostly at the gate and the ledger: monastery infirmaries stock Green Chain preparations, a surprising number of masters end their days as gate-sitters --- and since the Night of Cut Ledgers, every hall in Company country has been asked, by clients who never needed to ask before, where its records are kept, and in how many copies, and the Guilds have answered by adopting, without comment, the Companies' own triplicate custom, which the Table's minutes describe, in a rare flash of recorded humor, as \textit{a procedure validated elsewhere}.

\textbf{The Registries} hold the Guilds' enforcement account: mark-forgery writs, case-theft writs, and the fraud work --- and the two institutions, both temples of documentation, get along with the deep mutual comfort of clerks who have found other clerks.

\textbf{The Wardens} watch the grow-yards, as noted, and are watched back with gratitude the Green Chain is too professional to express: a spagyric yard that has begun drawing more than it was procedured to draw wants exactly one kind of visitor first, and it is not the Assay.

\medskip\hrule\medskip

\subsection{Current Fault Lines}

\begin{itemize}
    \item \textbf{The Argent Freeze.} Argent Line's banking arm has begun ``sequencing'' --- delaying, in perfect contractual correctness --- the dues remittances that flow from eastern halls to the Table, while offering to normalize the flow for any hall that signs preferential supply terms. It is the neutrality attacked through the plumbing: no side taken, no product touched, merely the federation's own blood chemistry adjusted from outside. Vance has so far answered with procedure --- escrow restructuring, remittance rerouting --- and the Table knows, and Argent Line knows the Table knows, that the next answer on the shelf is the one nobody has opened in eighty years.
    \item \textbf{The Dawn Paper.} A Coilwright Whyseeker --- Journeyman Essa Vael, twenty-six, appallingly rigorous --- has completed a replication study proving that the dawn clause of the standard Heart-quickening procedure is load-bearing: the quickening fails, at statistical certainty, when run in ignorance of the sky. The paper does not speculate. It does not need to; everyone who reads it hears the vim doctrine arrive. The Assay has sat on certification for five months, the Unblinking have somehow heard of it anyway, and Vael, who wanted only to know why, is discovering what the federation's exasperated tolerance looks like when it stops being exasperated and starts being frightened.
    \item \textbf{The Redwater Strike.} At the Redwater conversion works --- a Vault \& Coil floor running on Crucible licenses --- eleven workers are dead in a year to a refining procedure the Company has ``streamlined,'' and the licensed refiners have downed tools rather than run the unmarked variant. The Company holds a law-enforcement contract with a Mercenary Company whose commander is reading it very slowly; the Lions' local Rider has begun attending the picket, which changes its legal weather entirely; and somewhere in the hills above Redwater, it is said, Second Reading monks are watching, which changes everyone's.
    \item \textbf{The False Marks.} A forgery ring is selling unmarked Hearts under counterfeit Assay stamps through the Salt Reach rail towns, and the failures have started --- two dead at Endline, a freight yard burned at Dustline. The Assay has posted writs, doubled its examiners' escorts, and confirmed the detail it has not published: the forged stamps are struck from a genuine Assay die, retired, recorded as destroyed, in the rolls of a hall that no longer exists. The die is Harrow's.
    \item \textbf{The Overdrawn Yard.} A Green Chain vat-yard on the Verdant Belt fringe has reported --- to its credit, promptly --- that its newest frame line is maturing forty percent ahead of procedure, robust, gentle, flawless, and \textit{unaccounted for}: the yard is drawing growth it has not procedured from somewhere that is not in the recipe. The Wardens arrived without being sent for. The Warden who walked the yard's fence line spent a long time at the northwest corner, looking at the wild country, and what she said to the yard-master is now, in six weeks, the most-quoted sentence in the Green Chain: \textit{``Nothing is coming out. Something is} paying in\textit{. I'd want to know what it thinks it's buying.''}
\end{itemize}

\medskip\hrule\medskip

\subsection{The Guilds in Play}

\textbf{Playing Guild hands.} A Guild PC carries the federation's whole bargain in a satchel: craft that is real, portable, and wanted everywhere; a mark that is credit, identity, and liability at once; and the ladder's built-in campaign frame --- the \textbf{Walk}. A journeyman Tinkerer or Sawbones on the wander-years is the most naturally adventuring figure the setting produces: obligated to travel, welcome at every hall, collecting stamps and judgments, and honor-bound by the sending itself to come back knowing what the federation doesn't. The guild-of-origin choice does real character work (a Crucible Tinkerer and a Green Chain Tinkerer are different people before a word of backstory is written), and the neutrality supplies the recurring personal dilemma for free: the party takes sides. The mark must not. Carrying both is the character.

\textbf{What the Guilds pay adventurers to do.} Constantly, in coin, in craft, and in the favor-economy of an institution that fixes everyone's tools. Typical contracts, by tier:

\begin{itemize}
    \item Escort an Assay examiner on the circuit --- the classic contract: weeks of travel, a companion who can identify anything, and the standing certainty that someone on the route has a mark they need un-inspected.
    \item Run reagents: the Procedures eat rare inputs --- boundary salts, wild-country botanicals, storm-glass, the strange harvest --- and procurement from the places procurement is dangerous is the oldest line item in every hall's ledger and the single steadiest employer of adventurers in the setting.
    \item Recover a stolen case volume before its procedures are run by people who cannot read the injury annexes.
    \item Witness a first replication: a new procedure needs impartial observers, per Assay protocol, and the halls pay well for witnesses who are credible, discreet, and fast over open ground, in that order.
    \item Work the False Marks writs: trace the counterfeit Hearts up the supply chain toward whoever is holding a dead hall's die.
    \item Hold the line at Redwater --- for the strikers, for the Company, or for the Rider trying to keep the two apart; the Guilds themselves will pay only for the third, which tells you everything about the federation and does not make the job easier.
    \item Guard Journeyman Vael, who keeps declining to be guarded, to a hearing the Assay keeps declining to schedule.
    \item At the highest tiers: walk the Overdrawn Yard's northwest fence line with a Warden and a Green Chain master, out into the wild country, following the vigor upstream to whatever is paying in --- and be the kind of party that can bring the answer back in a condition the case libraries can use.
\end{itemize}

\textbf{Patrons.} \textit{An Assay examiner} --- steady contracts, spotless paper, and a professional's gift for noticing exactly what a party is: the examiner who trusts you is a reference that opens every hall in the federation. \textit{A Green Chain vat-master} --- the reagent runs, the frame drives, and, this year, the Overdrawn Yard's very quiet inquiries. \textit{Grandmaster Korvo Vance} --- for parties that have proven discreet twice: the Table's invisible-hierarchy errands, paid in favors banked against the day the party needs the federation, which, Vance observes while pouring, everyone eventually does.

\medskip\hrule\medskip
