% ============================================================
% TIMELINE — NEW CHAPTER (first draft)
% ------------------------------------------------------------
% CANON DECISIONS PROPOSED IN THIS FILE (all renameable):
%   - Dating system: Standard Reckoning (SR), from the Concord of
%     Carriers. Current year: 312 SR.
%   - The fall of nations: "the Unmapping." Mechanism: the Wild
%     answers territorial claims in proportion to their scale;
%     comprehensive mapping/claiming provokes. Explains both
%     statelessness AND why nobody maps end-to-end (regions.tex).
%   - Last nation: the Kingdom of Vasserein; its Grand Survey
%     triggered the final response.
%   - The "frontier fiction" (trade-companies.tex) originates as a
%     peace term of the First Boundary War.
%   - Named events: Long Night of Redoubt, Leo's Recognition, the
%     Sorrow of Vellhame, the Kindling, the Winter Concession.
%   - Meridian & Norther = the insolvent Company behind the Rust
%     Belt (regions.tex left it unnamed).
%   - Currency: the Ring, standardized at the Concord (picks up the
%     stray "1 Ring" reference in the Mairin species entry).
% ============================================================

\section{A Timeline of the Frontier}

\subsection{How Years Are Counted}

There is no royal calendar, because there are no kings. What there is instead is a contract.

In the year now called 1 SR, the surviving Trade Companies and the young craft Guilds met at a rail junction whose name is preserved only in the agreement they signed there, and standardized the two things that commerce across a stateless world cannot survive without: a common date and a common coin. The agreement is the \textbf{Concord of Carriers}. The date system is \textbf{Standard Reckoning}. The coin is the \textbf{Ring}. Every contract, bounty writ, Guild certification, and church ledger in the known regions is dated in SR, not because anyone loves the Companies but because a promise is worthless if two parties cannot agree on when it comes due.

The current year is \textbf{312 SR}.

Before the Concord lie the \textbf{Silent Years} --- the span between the fall of the old nations and the restoration of reliable record-keeping. How long the Silent Years lasted is genuinely unknown; a generation at least, perhaps three. Documents from that span exist, but they date themselves by calendars that died with the nations that kept them, and reconciling those calendars is a scholarly discipline with more practitioners than agreements. Everything before the Silent Years is history in the way the bottom of the ocean is geography: real, load-bearing, and mostly inferred.

\medskip\hrule\medskip

\subsection{Before Reckoning}

\subsubsection{The Fey Bargain (before memory)}

The oldest claim in scholarship, and the one with the worst sourcing: that magic entered the world through a bargain with the Fey, and that the price has not yet been paid --- or is being paid continuously, in a currency nobody has identified. No Enclave endorses this account publicly. No Enclave has refuted it. The Fey, who grow stronger on the stories mortals tell, have never confirmed or denied it, which the more careful scholars note is exactly what they would do in either case.

\textit{What remains:} everything, possibly. A debt nobody remembers is a debt that can still be called in.

\subsubsection{The Unmapping (the end of the old world)}

Nations existed once. The ruins of their capitals are quarried for cut stone; their roads underlie some of the rail beds; their border-forts stand in places that no longer border anything. What ended them was not a single war but a pattern, recognized only in hindsight: \textbf{the Wild answers claims in proportion to their scale.} A farmstead is tolerated. A town is watched. A nation --- a single will asserting ownership over land it has never walked --- is answered.

The old nations did not understand this. They expanded as nations do, and the answers grew with them, and the last and greatest of them, the \textbf{Kingdom of Vasserein}, sealed its fate with an act its scribes recorded as an administrative triumph: the \textbf{Grand Survey}, an attempt to map, name, and claim the entire interior in a single generation of cartography. The Wild's response to the Survey is the event the Silent Years are silent about. What is known is that Vasserein ended, that no nation replaced it, and that no institution since has attempted a comprehensive map of anything.

This is the fact underneath the setting's strangest habit: \textit{nobody maps end-to-end}, and the professionals who come closest --- Wardens, Pelorim, Gorûn route-keepers --- hold their knowledge in memory and fragments, never in a single document. Whether the caution is still necessary is debated. Whether anyone volunteers to test it is not.

\textit{What remains:} statelessness itself. Every institution in the current world --- the Companies' careful commercial fictions, the Houses' modest demesnes, the Guilds' property-without-territory --- is shaped like something the Wild will tolerate. The shape is not an accident. It is a survival strategy old enough to be mistaken for nature.

\medskip\hrule\medskip

\subsection{The Reckoned Centuries}

\subsubsection{1 SR --- The Concord of Carriers}

The founding act of the current order: standardized dates, the Ring, mutual recognition of contracts across Company territories, and the arbitration customs that would eventually mature into the Guild and Registry procedural frameworks. The Concord is not a constitution and was never meant to be one. It is a set of business terms that civilization grew around, which explains a great deal about civilization.

\subsubsection{118--126 SR --- The First Boundary War}

The first trunk-line era. Three Companies raced to lay competing lines westward into the great forests, claiming right-of-way in language that had drifted, over a century of confidence, back toward the language of nations. The Wild's response was coordinated across hundreds of miles --- the first proof since Vasserein that the Beast Lords could act in concert --- and it broke all three Companies and every settlement that depended on them.

The war ended not in victory but in the \textbf{Accord of Operations}: the surviving Companies formally renounced territorial claims and adopted the language of \textit{operations} --- lines run, stations maintained, services provided --- that they have used ever since. This is the origin of the frontier fiction that everyone maintains and nobody examines: the pretense that Company territory is not territory. The pretense was a peace term. Most of the people maintaining it no longer know that, which may be why it works.

\textit{What remains:} the Accord itself, unwritten into any current law but structurally present in everything. The Verdant Belt's hostility dates its modern form to this war. So, the Wardens believe, does the Beast Lords' practice of watching Company language as closely as Company construction.

\subsubsection{c.~151 SR --- The Long Night of Redoubt}

A demonic incursion overran the frontier town of Redoubt and was held --- barely, at terrible cost --- by a group of fighters and traveling priests who had arrived separately and stayed together afterward. The group became a company, the company an institution, and the institution, in time, the Witnesses of the Lion. The Lions date nothing from Redoubt officially, on the grounds that the founding recognition was never a single event, but every Lions chapter keeps the Long Night, and the keeping is older than the rank structure.

\subsubsection{168 SR --- Leo's Recognition}

Leo came to see the organization in person, found in it the central commitment of his own tradition, and gave it his name, his endorsement, and access to the church network's funding. The Lions insist on the direction of this event: he did not found them; he \textit{found} them. (See the Witnesses of the Lion chapter.)

\subsubsection{189 SR --- The Sorrow of Vellhame}

The containment catastrophe. A senior Arcanist of the Vellhame Enclave --- by every surviving account a careful, well-regarded practitioner --- suffered an accumulation cascade that neither he nor his Enclave arrested in time. The town of Vellhame, population somewhat over three thousand, was unmade in a single afternoon. Not burned: \textit{unmade}, in ways the relief expeditions spent years failing to describe consistently.

Vellhame is the reason. When a village fears the child whose nightmares scorch the bedsheets, when a mob forms faster than an Enclave's informants can reach a manifesting adolescent, when the Lions' harder voices ask what arcane magic \textit{is} --- Vellhame is the word underneath the argument. The Enclaves rebuilt their credibility across the following century through the informant networks, the containment protocols, and the doctrine of demonstrated usefulness that define them today. They have never disputed the fear. They dispute only the conclusion.

\textit{What remains:} the site, which is avoided; the protocols, which every Enclave drills; and the fear, which is patient.

\subsubsection{211 SR --- The Kindling}

The Enclave then called the Candlevault --- one of the oldest in the eastern regions, famed for its physical archive --- burned in a single night, with losses among its members that the survivors have never fully enumerated. The fire was not an accident and was not arcane. Beyond that, attribution has never been established. The survivors believed then, and their institutional descendants believe now, that the burning was the work of a hard-doctrine splinter within the Lions, acting in the fear-soaked decades after Vellhame. The Lions have never claimed the act, never been proven responsible, and never fully satisfied anyone --- including many Lions --- that the question was investigated as hard as it deserved.

The survivors made a collective decision never again to keep anything that could be burned. They have traveled ever since, and are known to everyone as the \textbf{Burning Library}.

\textit{What remains:} the Library itself, itinerant and unforgetting; a wound in Enclave--Lions relations that reopens on schedule; and, as of last year, the centennial --- observed by the Library in a form that was noticed (see Current Events, 311 SR).

\subsubsection{237 SR --- The Seat at Thirstgate}

The Lions established their frontier operational headquarters at Thirstgate, then a Company watering station, transforming it within a generation into the largest fortified settlement in the Iron Reach. The mortal Banneret has been seated at Thirstgate ever since.

\subsubsection{244--251 SR --- The Second Boundary War}

Larger, longer, and worse than the First. The precipitating cause is still argued --- the Wardens hold that a resource Company breached a sovereign territory in the north whose existence the Company's surveyors had dismissed as superstition; the Companies' records hold otherwise --- but the shape of the war is not argued: seven years of coordinated pressure across the entire northern and eastern rail network, the loss of dozens of settlements, and the insolvency of one of the era's great Companies, \textbf{Meridian \& Norther}, whose abandoned northeastern trunk line is now the haunted country everyone calls the \textbf{Rust Belt}.

The war ended in 251 with the \textbf{Winter Concession} --- a settlement brokered, remarkably, through intermediaries: Pelorim route-keepers and a handful of Wardens carried terms between parties that had no other channel. Among its provisions was the standing treaty that keeps Company expansion out of the Plains-of-the-Long-Walk, held jointly by the Pelorim and the Lions to this day.

\textit{What remains:} the Rust Belt, which the Wild came through and never left; the precedent that the Wardens and the plains peoples are the only functioning diplomatic channel civilization has; and the Lions' two-decade internal debate over whether reclaiming the Rust Belt is a duty or a provocation.

\subsubsection{259 SR --- The Fall of House Talvecq}

The ruling family of House Talvecq, of the central Dust Lanes, was destroyed --- the word is chosen carefully; \textit{killed} understates and \textit{annihilated} overstates --- over the course of what the official Lions account describes as a Shadow-leakage event that overwhelmed the House's defenses in a single night. The surviving Talvecq, none of whom were in residence, have never accepted the official account. Their reasons are specific: the House's defenses were built precisely against leakage events, had held against worse, and failed in a manner the survivors describe as \textit{answered} rather than overwhelmed.

Leo came to the site. This is documented. What he found, said, or did there is not: the account of his visit is the only record of a Leo appearance in the Lions' archive that is sealed, by his instruction, and the seal has held for fifty-three years.

\textit{What remains:} the Lost House; Severin Talvecq's twenty-year private investigation; and the seal, which every senior Lion knows exists and no senior Lion discusses.

\subsubsection{263 SR --- The Founding of Three Springs}

A religious community --- followers of the Grey Shepherd, by most accounts, though the settlement has never advertised its founding creed --- walked into the Hollow Marches, the most dangerous region on any map that doesn't exist, and built a town. Three Springs should not have survived its first winter. It has now survived forty-nine of them, within reach of the Hollow King's seasonal movements, and nobody --- not the Lions, not the Wardens, not Three Springs itself, as far as anyone can tell --- can fully account for why.

\subsubsection{283 SR --- The Glass Plains Measurement}

The Wyrd-leakage at the Glass Plains, long suspected, became \textit{measurable} --- instruments and Enclave techniques agreeing, for the first time, that the boundary there was thinning on a recordable trend. The Lions closed the Plains to Company exploration within the year, over sustained commercial objection, and have held the embargo since. House Vehk's centuries of observational records became, overnight, the most strategically significant private archive in the southern regions.

\subsubsection{294 SR --- The Broken Track}

The most serious modern attempt to drive rail through the Hollow Marches ended when the line's entire workforce --- three camps, some six hundred people --- was lost in a single night, with no incursion identified then or since. The Company abandoned the right-of-way. The partially built line remains where it was left. The Registries still carry a standing bounty, posted by families of the lost, that no certified Hunter has accepted in eighteen years.

\medskip\hrule\medskip

\subsection{Current Events (301--312 SR)}

\begin{itemize}
    \item \textbf{301 SR.} Cassien Vairo is elevated to mortal Banneret of the Witnesses of the Lion --- a moderate's appointment, made over hard-faction objection. His tenure, now eleven years, is the longest in a century.
    \item \textbf{303, 307, 311 SR.} Argent Line's fortified station at the Eastern Spur repels three separate major assaults. The Company has not published what assaulted it. The Wardens have theories. The theories do not agree.
    \item \textbf{307 and 310 SR.} Vault \& Coil's orichalcum-conversion facilities are attacked --- once by identifiable Wild forces, once by forces that were not identifiable, which is the detail everyone in the industry noticed.
    \item \textbf{311 SR.} The centennial of the Kindling. The Burning Library marked it by arriving, unannounced and in unprecedented numbers, in Thirstgate --- within sight of the Lions' seat --- observing a full night of silent commemoration, and dispersing by morning. No demands were made. Everyone understood it anyway.
    \item \textbf{312 SR --- the present.} Banneret Vairo's health is the subject of increasingly unquiet speculation. General Velgrim of the Long March is expected to name a successor within two years. The Glass Plains trend line has not flattened. And the Rust Belt question is once again on the agenda at Thirstgate, tabled by voices that were not, last time, senior enough to table anything.
\end{itemize}

\medskip\hrule\medskip
