% ============================================================
% TRADE COMPANIES — REWRITE
% ------------------------------------------------------------
% AUTHOR DIRECTION IMPLEMENTED:
%   - Tycoons, businessmen; no official class (yet); the setting's
%     natural employers and quest-givers.
%   - The class-less-ness is made thesis: the Companies' power is
%     organization, capital, and contract — the mundane
%     superpower — which is why they hire everyone else's
%     classes. The FACTOR (company agent who contracts outside
%     talent) is drawn as the setting's standard quest-giver
%     archetype; if a Company class is designed later
%     (Magnate/Factor), this niche is its slot.
% CANON DECISIONS PROPOSED (all revisable):
%   - Scrip economics: companies issue scrip/credit alongside the
%     Concord Ring; the "spread" (scrip discount vs Ring) is the
%     frontier's vital sign; scrip dies with its company
%     (Meridian paper as the ghost example).
%   - Company towns and the demographic time bomb: a generation
%     born in company towns for whom the Company is accidentally
%     becoming a faction — obligations the Companies never
%     wanted.
%   - Station clocks: the Companies keep civilization's time
%     (SR is theirs); clocks as their civic monument.
%   - New company: SOUTHREACH & AMBER — young, aggressive
%     speculative survey firm whose "Southreach Survey" is a
%     comprehensive southern mapping project: a Grand-Survey-
%     shaped ambition brushing the Unmapping taboo.
%   - New company (fault-line use): COASTAL & REACH — the
%     mid-register line whose scrip spread is blowing out.
%   - Kept from prior canon: Argent Line (Marcellus Argent; the
%     Freeze; Eastern Spur), Vault & Coil (Hesper Coil; Redwater,
%     the stockades, the monk bounty, the attacked works,
%     Serpent's Channel), Crossbow Holdings (Tessa Crossbow;
%     pays in Rings — the decent one), Meridian & Norther (dead,
%     249 SR).
%   - Cross-refs: timeline (Concord 1 SR, Accord of Operations,
%     threshold logic), Guilds (Freeze, licenses, Endline
%     Charter), Mercs (paper, Redwater ruling), Orders (Cut
%     Ledgers, triplicate custom), Houses (Ardenne seals, Ophara
%     arbitration, Varn survey), Wardens (assessments),
%     Registries (Greywater docket).
% ============================================================

\section{The Trade Companies}

\subsection{Origins}

Ask what replaced the nations and every faction in this book will give you a different answer, and the Companies' answer is the only one with documentation: \textit{we did, on page one.}

The Concord of Carriers is the founding act of the current order, and it is a business instrument --- a standardization of dates, coin, and contract recognition among freight concerns --- and everything civic about the reckoned centuries is downstream of it. The year is a Company convention. The Ring is a Company coin. The arbitration customs that grew into the Convention and the Registries' evidentiary practice began as shipping clauses. The Companies did not seize civilization's commanding heights; they \textit{scheduled} them, and three centuries later the schedule is the nearest thing the stateless world has to a constitution: the rails run, the manifests clear, the station clock in every town of consequence is wound, certified, and owned by a Company, and when the frontier asks \textit{what time is it}, the honest answer --- the Companies have never once made this joke in public, which tells you they know it is not a joke --- is \textit{ours.}

And yet. The founding generation's other document is the one the Companies teach their principals first: the \textbf{Accord of Operations}, the peace that ended the First Boundary War, in which the surviving Companies renounced the language of territory forever and adopted the language of \textit{operations} --- lines run, stations kept, services rendered --- because three of the era's greatest concerns had just been broken for talking, and building, like nations. The Accord is why the Companies are what they are: state-shaped things filed, permanently and deliberately, under commerce. The filing is not modesty. The filing is survival --- the threshold arithmetic every institution in this world answers to, applied at the largest scale anything dares --- and the deepest fact about the Companies is that most of the people running them no longer know it. The frontier fiction (that Company country is not territory, that the towns are not subjects, that the greatest concentrations of power in the world are merely \textit{firms}) was a treaty term. It has been maintained so long, so successfully, that it is maintained now by pure institutional reflex, by principals who think it is politeness and clerks who think it is style --- and the handful of people who remember what it actually is (certain Wardens; the Antler, presumably, in some column of the count; one or two very old hands per boardroom) watch the young tycoons chafe against the fiction's constraints with the specific horror of people watching someone lean on a door without asking why it was locked.

Power real and shallow, simultaneously. That is the Companies, and both halves are exact. Real: the rails, the fleets, the works, the banking arms, the scrip in a hundred thousand pockets, the capacity to move grain, iron, and consequence across distances no other institution can address. Shallow: no one is \textit{of} a Company. The Lions have their sworn, the Houses their blood, the Guilds their marked, the network its walks --- and the Companies have employees, who are of somewhere else, and clients, who are counting. A Company commands everything it can pay for and holds nothing it cannot, and the whole edifice rests, as its own actuaries will tell you in the right mood, on the continued willingness of everyone else to keep being paid.

\medskip\hrule\medskip

\subsection{The Ledger and the Line}

A Company is capital organized around a flow --- freight, energy, credit, salvage --- and its anatomy is consistent across the register: the \textbf{principals} (founders, partners, the board --- the tycoons, of whom more below); \textbf{operations}, which is the visible Company --- the lines, works, yards, and stations; the \textbf{security paper}, contracted to the Mercenary Rolls, because in-house musters are the conflict of interest every actuary prices and every principal periodically re-discovers; the \textbf{banking arm}, where the real leverage lives; and the \textbf{factors} --- the Company's standing agents in every town its flow touches, of whom much more below, because the factor is where the Companies and an adventuring party meet.

The economics run on two kinds of money, and reading the gap between them is the frontier's actual news service. The \textbf{Ring} is the Concord coin: universal, neutral, and scarce out past the trunk lines. \textbf{Scrip} is Company paper --- wages paid in it, company stores pricing for it, credit extended in it --- good exactly as far as its issuer's health and reach, and traded against the Ring at the \textbf{spread}: the discount that every station moneychanger chalks up daily and every trader three regions wide reads like a pulse. Tight spread, healthy Company. Widening spread, trouble on the line before the line knows it. And the spread's far end is the lesson every frontier family owns a physical copy of: somewhere in a drawer, in half the households of the northeast, there is still Meridian \& Norther paper --- crisp, beautifully printed, and worth precisely nothing since one week in 249 SR --- kept not as hope but as instruction, the frontier's own memento: \textit{scrip is a promise, and promises have issuers, and issuers can die.}

Around the scrip, the \textbf{company towns}: the settlements the flows called into being --- rail-head, works-town, depot --- built on Company ground, paid in Company paper, provisioned at Company stores, and constituting the fiction's finest print. A company town is not territory (the Accord); its people are not subjects (obviously); the Company owes them wages, not protection, justice, or futures (the contracts are clear) --- and the towns exist anyway, and fill with children anyway, and the children grow up anyway, and the Companies have thereby acquired, without ever once agreeing to, the thing their whole architecture was designed to avoid: \textit{a people.} There is now a generation in the works-towns --- Redwater is full of them --- born on Company ground, schooled in Company sheds, whose only community, first loyalty, and entire inherited world is a firm that is contractually not their home; and what those children are owed, and by whom, and what they will do about the answer, is the question underneath every labor fault line in this book, and the Companies' boards have exactly no doctrine for it, because having a doctrine for it would mean admitting what they have accidentally grown.

\medskip\hrule\medskip

\subsection{The Tycoons}

Here is the strangest fact about the most powerful individuals in the world: they have no power at all.

No art. No gift. No eruption, blood, cultivation, shapes, or Read --- the tycoons are the setting's great unarmed, ordinary flesh in a world of Dynasts and Magisters, and the tradition's own hands say it with a pride that is entirely earned: \textit{there is no Company art; there are Company} people. What a tycoon holds is organization --- the ledger, the schedule, the credit line, the ten thousand employees, the learned, teachable, terrifying craft of making arrangements that outlive their maker --- and the honest ranking of consequence in this world puts a first-rank principal above any Magister and most sovereigns, achieved with nothing but ink. The other factions find this alternately contemptible and unnerving, and the unnerved are correct: everything else in this book is bounded by its power's nature --- the mass accumulates, the blood breeds true or thin, the hearth holds what it holds --- and the ledger is bounded by \textit{nothing except other ledgers}, which is why the Wild's threshold, the Accord's fiction, and the other factions' vigilance are, jointly, the only walls the Companies have ever respected.

And because the tycoons have no art, they \textbf{buy everyone's}. This is the Companies' deepest relationship with the rest of the setting and the reason this faction, alone, is written frankly as an employer: the Companies contract Guild procedure, Mercenary paper, Enclave warding, Warden assessment, Registry inquest, House guarantee --- and, below all the institutional paper, at the retail level where campaigns live, they hire \textit{adventurers}: the flexible, deniable, capable outside talent for the ten thousand problems that are too small for a contract, too strange for a department, or too quiet for either. No faction generates more work for a party, more variously, with fewer questions --- and no faction's work carries less protection, which is the trade in one line, and the factors quote it themselves, with a smile, at signing: \textit{the Company's memory is exactly as long as the engagement.}

\medskip\hrule\medskip

\subsection{The Factor}

Every town on a Company's flow has one: the \textbf{factor} --- the standing agent, the fixer, the face --- keeping the Company's local book, smoothing the Company's local frictions, and holding the Company's local budget for \textit{problems}, a word factors use with great professional breadth.

The factor is the setting's quest-giver made flesh, and the office deserves its anatomy. A factor's authority is real and capped (they can contract, up to a line; above the line, they write to the principals, which takes weeks the problem rarely grants); their information is superb and local (the factor knows who arrived, who is capable, who is desperate, and which of the three describes the party); their incentives are exquisitely legible (a factor's book is audited on outcomes, so a factor wants problems \textit{solved}, cheaply, quietly, and in a manner that reads well in the ledger, in that order); and their culture is a guild in all but charter --- factors of rival Companies dine together in every station town, trade talent the way stables trade tack, and maintain, across all commercial hostility, the one professional courtesy the whole trade runs on: an honest reference. A party that does clean work for one factor is, within a season, known to every factor on the line. A party that embarrasses one is known faster.

What comes across a factor's desk, in the ordinary course: freight that must move through country the paper won't cover; a branch-line problem the word \textit{problem} is doing heavy work to describe; a survey that needs guarding, a surveyor that needs finding, a station master's ledger that needs auditing by someone the station master has never met; recoveries, escorts, deliveries with sealed manifests; the rival factor's business, learned about discreetly; and, perennially, the local troubles a Company inherits by being the biggest thing in town --- the missing children, the strange lights over the yard, the thing eating the telegraph line --- which the Company does not owe anyone the solving of, and which a good factor solves anyway, because towns that trust the factor cost less to operate in, and \textit{that} arithmetic, at least, the boards have always understood.

\medskip\hrule\medskip

\subsection{The Companies}

The register carries hundreds of charters. Four, and one grave, define the current landscape.

\subsubsection{Argent Line}

The great rail-and-banking concern of the east: the trunk lines out of Thirstgate, the Eastern Spur, and, increasingly and by design, the credit architecture underneath everyone else's operations --- Argent's banking arm holds paper on half the register and remittance relationships with institutions that would prefer not to discuss it (the Guild dues affair, called the Freeze, is the current test of exactly how far that leverage stretches). The Line's public face is \textbf{Marcellus Argent} --- third-generation principal, the register's finest political operator, a man who has spent thirty years proving that the softest voice in the room can hold the biggest book --- and its current mystery is its own flagship asset: the fortified station at the Eastern Spur has repelled three major assaults in nine years, the Line has never published what assaulted it, the Wardens' theories do not agree, and Marcellus's only recorded comment --- \textit{``the Spur is adequately provisioned''} --- has been repriced by the market roughly monthly since he made it.

\subsubsection{Vault \& Coil}

The industrial giant: orichalcum conversion, Heart manufacture at scale, the works-towns of the Salt Reach and southern Reach --- and the register's hard case, in every sense. V\&C runs the frontier's most essential industry with the register's harshest labor book (the stockades, the streamlined procedures, the Redwater dead), and its year has been an education in consequences arriving in convoy: the Convention asked to rule on its Redwater paper, its debtors' ledgers already once cut by monks it has since priced privately (a bounty the Registries have formally noted and the Rolls formally deplore), its conversion works attacked twice --- once by the Wild, once by something no one has identified --- and its orichalcum barge sitting in the Serpent's Channel being unloaded by the deep. The principal is \textbf{Hesper Coil} --- Tikka, the finest works-engineer of her generation, a founder who built the conversion process with her own hands and has spent twenty years discovering what the process built around her --- and the register's oldest running argument is whether Hesper Coil is the author of V\&C's harshness or the last thing restraining it. The people who deal with her directly hold the second opinion, worriedly.

\subsubsection{Crossbow Holdings}

The freight-and-security house of the west, and the register's standing proof that the other model works: Crossbow pays in Rings --- no scrip, ever, a founding rule --- runs the cleanest labor book on the register, prices accordingly, and profits anyway, a fact its principal declines to draw morals from in public and has built an empire on in practice. \textbf{Tessa Crossbow} --- unaffiliated her whole life, a Mercenary commander before she was a principal, the only tycoon on the register who has personally held a wall --- founded the house on the insight her first career taught her: \textit{reliability is the scarcest commodity on the frontier, and the margin on scarcity is infinite.} Crossbow factors have the register's best reputation among adventurers (clean contracts, prompt Rings, honest references), the house's convoys are the safest paper a young party can ride --- and the register's quietest current question is the succession, because Tessa is seventy-one, has built no dynasty on principle, and has begun receiving, with visible amusement, acquisition courtesies from Argent Line, whose interest in owning the register's reputation for decency is, everyone agrees, the most sincerely alarming compliment in recent commercial history.

\subsubsection{Southreach \& Amber}

The young one: a speculative survey-and-ventures house, six years chartered, capitalized out of the southern salvage boom, and run by principals with excellent educations and no memory --- which is the point of the entry. Southreach's portfolio is the frontier's edges (Greywater margin rights, Salt Reach prospects, route options south of the Varn Gap that House Ostrogar has not yet learned about), its methods are aggressive and its Warden assessments are, by the network's published tally, the most frequently ignored on the register --- and its flagship undertaking, announced with prospectus and fanfare, is \textbf{the Southreach Survey}: a comprehensive, standardized, end-to-end cartographic project for the entire southern country. \textit{Comprehensive.} The prospectus uses the word eleven times. Every institution with a memory --- the Wardens, the Houses, the older boards, anyone who has read the Timeline's first pages --- has reacted to the Survey with a horror the young principals find theatrical and their own oldest hands have quietly begun resigning over; the Wardens' formal assessment of the project ran to one sentence (\textit{``The last institution to attempt this is why there is a Timeline''}); and Southreach's answer, delivered by its brilliant, laughing, thirty-four-year-old managing principal, is the sentence on which some considerable portion of the world's future may currently rest: \textit{``Gentlemen, it is} superstition\textit{, and the margin on superstition is infinite.''}

\subsubsection{Meridian \& Norther (struck, 249 SR)}

The grave, kept on the register by custom, as instruction. The great northeastern concern; the Second Boundary War; the insolvency; the Rust Belt; the scrip in the drawers; the columns never discharged. Every Company on the register is one bad decade from this entry, and the register knows it, and the entry is re-inked, by rotating custom, at every annual convocation, by the youngest principal present, by hand.

\medskip\hrule\medskip

\subsection{The Companies Among the Factions}

\textbf{The Guilds} are the dependence the Companies resent most and need most --- licenses, Hearts, marks, the whole procedural substrate --- and the Freeze is the register's first open attempt to convert financial plumbing into leverage against it. The halls have noticed. The shelf is dusted.

\textbf{The Mercenary Rolls} hold the security paper, and the Redwater memorandum has put the register's whole enforcement portfolio under a question the Convention will now have to answer in general terms: \textit{what does a client buy?} The boards filed briefs. The boards are, privately, as frightened of a broad answer as of a narrow one.

\textbf{The Lions} and the register meet at the church-funding tangles, the vim doctrine (a theology of technology is a theology \textit{of the Companies' inventory}, and the boards have finally noticed), and the mainline's patient insistence --- Rider by Rider, picket by picket --- that the towns the Companies do not owe anything to are nonetheless full of people the Lions do.

\textbf{The Houses} are fixed terrain, as ever: the Ardenne seals that make Company promises credible, the Ophara arbitration, the Varn survey that had better stay quiet, and the standing asymmetry that a House is small, old, and loved, and a Company is vast, young, and \textit{counted on}, and both know which survives a bad generation better.

\textbf{The Enclaves} sell warding and buy tolerance; the Endline Charter model (Company-adjacent training, service contracts) is the register's favorite development in a century and the Convocation's least; and every board has, somewhere, the memorandum estimating what a house Arcanist program would save, and every board has, so far, filed it, because Vellhame is on the Timeline too.

\textbf{The Wardens} price the register's whole frontier: the assessments, the integrity clause, the weariness --- the network's Company files are administered by Wardens with the specific patience of people who have repeatedly explained why a route will not work and then watched it be tried --- and the Southreach Survey has unified the network's opinion of the register in a way nothing has since the Second Boundary War.

\textbf{The Registries and the Orders} hold, respectively, the register's paper edges (the Greywater docket, the writ-work on absconding treasurers) and its newest nightmare: an institution whose blades cut records has made every board in the world think, for the first time, about what its ledgers physically \textit{are} --- and the triplicate custom now spreading through the register is the first tribute, the Second Reading observes, that capital has ever paid to a vow of poverty.

\medskip\hrule\medskip

\subsection{Current Fault Lines}

\begin{itemize}
    \item \textbf{The Southreach Survey.} Funded, staffed, launching in spring: the first comprehensive mapping project since the Grand Survey ended the world that attempted it. The Wardens have refused all assessment and guiding contracts --- the network's first total refusal on record --- the older boards are quietly shorting Southreach paper, and the only institutions that could stop it are institutions that would have to explain, in public, \textit{what exactly they believe will happen}, which is the one sentence three centuries of the fiction have made unsayable.
    \item \textbf{The Freeze, Escalating.} The Guilds have rerouted remittances; Argent's banking arm has responded by sequencing something new --- the escrow flows of the Convention's arbitration accounts, which touches the Mercenary Rolls, the Registries, and every institution that ever parks money between promises. Marcellus Argent is now leveraging the plumbing of the stateless order itself, and the register's oldest hands are watching for the moment he discovers what the order's other institutions consider that plumbing to be worth.
    \item \textbf{The Coil Convergence.} Redwater, the stockade bounty, two attacked works (one attacker still unidentified), the emptied barge --- the register's essential Company is absorbing pressure from five directions at once, and Hesper Coil has begun asking, in the private way that founders ask, whether the directions are directions or a \textit{pattern}: whether something is squeezing Vault \& Coil specifically, and if so, whether it wants the Company broken --- or merely wants the Company's founder to finally lose the argument she has been winning, barely, at every board meeting for twenty years.
    \item \textbf{The Dustline Discount.} The spread on Coastal \& Reach scrip --- a mid-register Salt Reach line --- has widened from two points to eleven in a season, for reasons the moneychangers cannot source, and the run dynamics are loading: the towns on the C\&R line hold their savings in its paper, the company store credit is denominated in it, and the frontier has seen this exact chalkboard before, in 249, and knows how fast the last three points go. Someone is either killing Coastal \& Reach or profiting from its death-rattle, and the factors of four rival Companies are all in Dustline this month, which the moneychangers have also noticed, and chalked.
    \item \textbf{The Towns' Question.} Redwater's picket held. The Convention will rule. And in a dozen works-towns the register's accidental people --- the company-born generation --- have started holding meetings the factors' reports struggle to classify: not strikes, not congregations, not factions. \textit{Yet}, notes the one factor's report the boards keep re-reading, a Crossbow hand of thirty years' service, in the last line her principals have not answered: \textit{``They are deciding who their people are. Every institution in this world was born the same way. I have watched it happen. Recommend we decide what we are to them before they decide it for us.''}
\end{itemize}

\medskip\hrule\medskip

\subsection{The Companies in Play}

\textbf{Playing Company people.} There is no Company class --- yet; the niche is real and may someday be filled --- and the faction is playable anyway, three ways. As \textbf{background}: the company-born character, the ex-factor, the surveyor, the clerk who saw the wrong ledger --- origins that hand a PC the register's textures (scrip literacy, the spread, the factors' web) and its accidental-people question as personal stakes. As \textbf{patron-relationship}: the party as a factor's standing talent, the campaign frame with the setting's most renewable job engine built in. And as \textbf{antagonist-employer}: the register's work is the setting's best morally-loaded paycheck --- clean coin for jobs whose cleanliness is the party's problem to determine --- and a campaign can run a long time on the distance between what the factor contracted and what the party found at the branch line's end.

\textbf{What the factors pay adventurers to do.} Everything; that is the faction. A working sample, by tier:

\begin{itemize}
    \item Ride a Crossbow convoy: the register's cleanest paper, prompt Rings, and the reference that opens the factors' web.
    \item Solve a branch-line problem: the freight stops at mile forty, the linemen won't say why, the factor's budget says \textit{quietly}.
    \item Audit a station: books, stores, and a station master who has been paying something that isn't on any manifest.
    \item Guard a spread: the C\&R chalkboard work --- escort the moneychangers' courier, find who is dumping paper, and learn how a bank run smells the day before.
    \item Carry a sealed manifest: contents unstated, route specified, questions priced into the fee, which is generous.
    \item Work the Coil pattern: Hesper Coil is quietly contracting outsiders to determine whether her Company's terrible year has an author --- the register's best-paying investigation and its most dangerous, in proportions the party will discover.
    \item Decline the Southreach retainer --- or take it: the Survey pays triple, its escort contracts are the register's most lucrative open paper, and every Warden, elder, and old hand the party has ever earned the respect of will know.
    \item At the highest tiers: be in Dustline when the last three points go; be at Redwater when the Convention rules; or carry, for a factor of thirty years' service, one unanswered report past her principals to someone --- the party's choice of someone --- who will.
\end{itemize}

\textbf{Patrons.} \textit{A factor} --- any factor: the archetype is the patron, renewable, local, audited on outcomes, and the campaign's most honest NPC relationship, because the party will always know exactly what the factor wants, which is the problem solved and the ledger clean, in that order, and the drama lives in the days those two goals part. \textit{Tessa Crossbow} --- for parties with reputations: the register's decent empire runs on talent it can trust out of sight, pays in Rings and references, and its founder's personal commissions, lately, have all concerned the question of what Crossbow Holdings becomes when she is gone. \textit{Marcellus Argent} --- for parties that have been noticed: the softest voice in the register hires rarely, briefs completely, pays magnificently, and has never once told anyone the whole of what the job was for; the parties that work for him twice are the parties that have made their peace with that, and the register watches who they are.

\medskip\hrule\medskip
