% ============================================================
% THE UNAFFILIATED — REWRITE (short chapter)
% ------------------------------------------------------------
% AUTHOR DIRECTION IMPLEMENTED:
%   - Not a faction: the absence of one. Deliberately brief; no
%     exemplar/fault-line sections (nothing to have them about).
%   - Most people are unaffiliated. ADVENTURERS rarely are — new
%     framing: every power in the setting has an institution
%     that comes looking (the nets), so an unaffiliated adventurer
%     slipped every net or left one, and that fact IS the story.
% CANON NOTES:
%   - Kept from the original: the Defected/Rejected/Chosen
%     patterns; "most people are unaffiliated" as the grounding
%     move.
%   - Welds: the nets (Enclave informants/Returns, the walkers,
%     Warden vouching, Guild binding, bench certification,
%     blood-book recognition, Rider sponsorship); bare vs
%     unaffiliated distinguished (Hoppean); effacement as forced
%     unaffiliation; the Witch-Roads and the factors' web as the
%     informal economy; Tessa Crossbow and Mira Theoden as the
%     Chosen pattern's proof cases; the party-as-proto-faction
%     closing note.
% ============================================================

\section{The Unaffiliated}

\subsection{The Baseline}

This chapter describes most people in the world, which is why it is the shortest one in the book.

The factions are not the population. They are the population's \textit{institutions} --- and the farmer outside Lastlight, the moneychanger at the Dustline station, the midwife, the lineman, the innkeeper, the child: none of them is sworn, marked, chartered, Read, or entered in anyone's rolls, and none of them is missing anything. The unaffiliated majority has what humans have always had --- family, town, congregation, trade, neighbors --- and the question the factions answer (\textit{who are your people, beyond the horizon of the people you can see?}) is a question most lives never need to ask. A faction is what you need when your obligations, enemies, or capabilities outgrow your village. Most obligations don't. Most people's don't. The unaffiliated are not the setting's leftovers; they are the setting --- the ground the factions stand on, recruit from, and exist to serve, protect, bill, and occasionally frighten.

So being unaffiliated is not a condition, requires no explanation, and carries no membership: there is no unaffiliated hall, creed, or sign, and the moment there were, it would be a faction, and this chapter would be one page shorter. What the condition \textit{does} carry is a boundary worth stating exactly, because the trades blur it: unaffiliated is not \textbf{bare}. The bare are the uninsurable --- the people no Company will paper, whom conduct has priced out of every web --- and that is a verdict, not a status. The unaffiliated buy coverage, hold Guild-marked tools, post at the Registry, and pray at the funded church like anyone; they are clients of everything and members of nothing, and the whole commercial architecture of the stateless world was built, precisely, so that membership would never be the price of participation.

\medskip\hrule\medskip

\subsection{The Nets}

Here is the asymmetry this chapter turns on: most \textit{people} are unaffiliated, and most \textbf{adventurers are not} --- because in this world, capability is found.

Every power the setting contains has an institution whose first function is locating it. The Enclaves' informant web reaches the manifesting child before the village does. The walkers carry standing instructions about wild blades. The Wardens find the boundary-crossers the recognition has touched. A Guild hall binds promising hands at fourteen. The benches certify the Read before it certifies itself. The blood-book knows its own before they are born, and the visible gift, by definition, cannot slip away into a crowd. Even the Lions --- the one great power that must be chosen --- run their sponsorship through Riders who know every family on the circuit. The setting's institutions are, among everything else they are, a collective talent-finding machine of three centuries' refinement, and its net is woven exactly at the scale of an adventurer: someone whose capabilities have outgrown their village is someone the appropriate institution has, in the ordinary course, already met.

So the unaffiliated adventurer is rare, and the rarity is informative: they slipped every net, or a net let them go, or they cut their way out of one --- and whichever it was is the most important fact about them. The old field taxonomy still serves, refreshed:

\textbf{The Defected} left. The released Lion (honorable; the sigil's welcome keeps); the monk who walked back out the gate (which does not close behind them); the journeyman who never came home from the Walk; the Warden who chose the inside. Defection is common at the small scale and clean at the honorable end --- most institutions maintain dignified exits, and a character who took one carries their formation without its obligations. The other end is not clean: the severed Lion, the expelled hall, the effaced name --- the forced unaffiliations, in which the institution did not lose a member but \textit{amputated} one, and a character carrying that history is carrying the setting's heaviest and most interesting baggage, because forced unaffiliation is the one kind everyone can eventually find out about.

\textbf{The Rejected} were never taken. The candidate the Reading unsettled; the apprentice no master bound; the boundary-crosser the Gather, for once, did not concur on; the House child the blood passed over who then declined the steward's desk. Rejection leaves a shape --- the capable person shaped by the institution that would not have them --- and it matters at the table in ways clean defection does not: the Rejected still speak the institution's language, still want or hate or grieve it, and are still, often, better at its business than half its members, which the institution notices, eventually, awkwardly.

\textbf{The Chosen} simply refused, and the pattern's proof cases run the whole scale of the world: Tessa Crossbow, unaffiliated for seventy-one years, holding the register's cleanest empire; Mira Theoden, unaffiliated her entire career, commanding a chartered Company because the Rolls license capability, not belonging. The Chosen demonstrate the condition's honest upside --- the unaffiliated are the only people in the world who can work for everyone, be trusted \textit{as} no one's, and owe their judgment to nothing but themselves --- and its honest price, which the Chosen pay knowingly: when it goes wrong, no chapter house shelters them, no Concord intercedes, no Gather grieves. The Chosen are betting a lifetime that they will be enough. The interesting ones are the ones who know the size of the bet.

\medskip\hrule\medskip

\subsection{The Loose World}

No hall, but not no world. The unaffiliated who work --- the freelancers, fixers, guides, guards, and adventurers-between-things --- move through an infrastructure that belongs to nobody and functions anyway: the \textbf{factors' web}, which hires the unaffiliated gladly and references them honestly, and constitutes, for a capable outsider, the nearest thing to a career ladder the loose world offers; the \textbf{station taverns} and posting boards where work finds workers; the \textbf{Witch-Roads} and the other old paths where the loose world's own specialists --- the hedge-practitioners, the road-wise, the uncredentialed and unclaimed --- keep customs older than the Concord; and, everywhere, \textbf{the word}: reputation carried mouth to mouth, the loose world's only mark, slower than an Assay stamp and, the factors will tell you, no less accurate over a season. The unaffiliated practitioner of a housed art lives on this infrastructure at a particular angle --- the wild blade whom walkers keep visiting, the unsanctioned Read the benches keep monitoring, the hedge-shifter the network keeps meaning to vouch --- welcome in the loose world and \textit{watched} from the institutional one, which is not hostility, exactly. It is the net, still open, being polite about it.

\medskip\hrule\medskip

\subsection{In Play}

An unaffiliated PC is a deliberate choice and should be played as one: the character has no chapter house, no bench, no Gather --- and no claims on them, no doctrine over them, and no institution's enemies inherited at first level. The build questions are the taxonomy's: which net, and what happened at it. And the campaign pressure is built in, because the nets stay open --- the walkers visit, the factors offer, the House writes --- and an unaffiliated adventurer of rising capability is a person the institutions court with increasing seriousness, which means the character's defining choice gets re-asked, at higher stakes, for the entire campaign. Refusing a faction once is a backstory. Refusing it every season, as the offers improve, is a character.

One last observation, offered to the table rather than the setting. An adventuring party --- people bound by shared obligation, mutual protection, pooled reputation, and the answer to \textit{who are your people} --- is not unaffiliated at all, whatever its members' papers say. It is a faction of four, at the first size a faction comes in, running on the same architecture as everything else in this book; and every institution the party deals with will, sooner or later, treat it as exactly that. The factions were all small once. The Lions began as a company that survived something together and stayed. It is worth knowing, at the table, that the setting's history offers no examples of that stopping where it started.

\medskip\hrule\medskip
