% ============================================================
% CHARACTER CREATION & CLASS STAT LINES — FIRST DRAFT
% (Rulebook Ch. 5 + the stat-line half of Ch. 7)
% ------------------------------------------------------------
% Fills the outline's #1 blocking-play gap: creation arrays,
% per-class derived stats, and Moderate/Major threshold values.
% All numbers are tuning stakes, sanity-checked by simulation
% (see Design Notes) against the combat chapter's wound math.
%
% [PROPOSALS FLAGGED FOR SIGN-OFF]
%   CC1. Arrays: Skills 20 points (cap 4 at creation); Alignments
%        10 points (cap 3 at creation). The 5+ "supernatural
%        influence" threshold is meant to be EARNED — with one
%        exception: each class names a Signature Skill that may
%        start at 5 by spending points to 4 and taking the class's
%        +1.
%   CC2. Class stat lines (table below): Strike/Shoot targets
%        3+–5+, Defend 0–2, Move 4"–5", thresholds Mod 3–5 /
%        Maj 7–10.
%   CC3. Tiles→inches: older species traits written in tiles read
%        1 tile = 2" (Pelorim base 4", Korr fly 6").
%   CC4. Leveling ladder (table below): +2 cards & 1 swap every
%        level; +1 skill point every level; deed rank at even
%        levels; +1 Alignment point at L3/6/9; +1 Moderate & +1
%        Major threshold at L4 and L8; +1 to one of Strike/Shoot/
%        Defend (once each) at L5/L7/L9.
%   CC5. DEED CONVERSION (errata to deeds.tex): Deathproof's HP
%        bonuses become thresholds — I: +1 Moderate; II: +1 Major
%        and +1 die on saves at or past your Moderate count...
%        simplified below. All other HP references in cards read
%        "damage/healing" against wounds per the sidebar.
%   CC6. Healing in a wound system (interim rule until Ch. 13):
%        "Heal N HP" on existing cards reads "reduce one wound's
%        severity one step per 3 healing, or clear one minor per
%        2" — simplified sidebar rule below.
% ============================================================

\chapter{Creating a Character}

\section{The Eight Steps}

\begin{enumerate}
    \item \textbf{Choose your species.} Take its trait; note its 5-card pool. (Chapter: \textit{The Seventeen Peoples}.)
    \item \textbf{Choose your class and archetype.} Note your class stat line (below), your Signature Skill, and choose 10 cards from your archetype's pool (level-1 cards; duplicates as marked).
    \item \textbf{Choose your faction} --- or none. Take the 5 faction cards, or the Drifter set, and know who your people are.
    \item \textbf{Rate your Skills.} Distribute \textbf{20 points} across the twelve skills, \textbf{maximum 4} in any one. Then apply your class's \textbf{+1 Signature Skill} bonus --- the one place a starting character may stand at 5, already past the line the world calls supernatural influence.
    \item \textbf{Rate your Alignments.} Distribute \textbf{10 points} across the five planes, \textbf{maximum 3} in any one. Every point is a relationship; the GM is invited to remember all of them.
    \item \textbf{Write your Identity.} Demeanor (how you present), Drive (what moves you), and a Reputation the GM co-signs and thereafter owns. Leave the wanted-poster line blank if you dare.
    \item \textbf{Take your kit.} Each class lists a starting kit in the Equipment chapter; note your Armor line (X+/Y+), weapon lines, and 10 Rings walking money.
    \item \textbf{Assemble the deck.} 20 cards. Shuffle. Holster. You're on the frontier.
\end{enumerate}

\medskip\hrule\medskip

\section{Class Stat Lines}

Your class sets the combat line and the two damage thresholds. (Targets: lower is better. Defend subtracts attacker dice. Thresholds: damage at or past \textbf{Mod} is a moderate wound; at or past \textbf{Maj}, major.)

\begin{center}
\small
\begin{tabular}{l|cc|c|c|cc|l}
\textbf{Class} & \textbf{Strike} & \textbf{Shoot} & \textbf{Defend} & \textbf{Move} & \textbf{Mod} & \textbf{Maj} & \textbf{Signature Skill} \\
\hline
Zealot & 3+ & 4+ & 1 & 4" & 5 & 10 & Religion \\
Circuit Rider & 4+ & 4+ & 1 & 5" & 4 & 9 & Convince \\
Arcanist & 5+ & 4+ & 0 & 4" & 3 & 7 & Study \\
Dynast & 3+ & 4+ & 1 & 5" & 5 & 10 & Intimidate \\
Monk & 3+ & 5+ & 2 & 5" & 4 & 8 & Nimbleness \\
Tinkerer & 5+ & 4+ & 0 & 4" & 4 & 8 & Knack \\
Sawbones & 4+ & 4+ & 0 & 4" & 4 & 8 & Study \\
Captain & 4+ & 3+ & 1 & 4" & 4 & 9 & Convince \\
Bounty Hunter & 4+ & 3+ & 1 & 5" & 4 & 8 & Survive \\
Shapeshifter & 4+ & 4+ & 1 & 5" & 4 & 9 & Folklore \\
\end{tabular}
\end{center}

\textit{Reading the spread:} the martial callings (Zealot, Dynast, Monk) close and endure; the trigger professions (Captain, Bounty Hunter) shoot at 3+; the bench classes (Arcanist, Tinkerer, Sawbones) are dangerous through their decks and \textbf{fragile in the open} --- an Arcanist at Mod 3/Maj 7 treats a pistol ball as a moderate wound from the first hit, which is the correct amount of afraid. Shapeshifter values are the walker's own body; worn forms use the form's line per the class rules.

\textbf{Species adjustments.} Species traits modify where they say (Pelorim Move 4" base and quadruped rules; Korr fly 6" per their trait's limits; Gorûn and Serekh count as Large where equipment cares). Older trait text written in \textit{tiles} reads 1 tile = 2".

\medskip\hrule\medskip

\section{Advancement}

\begin{center}
\small
\begin{tabular}{l|l}
\textbf{Every level} & +2 cards (any of your pools, card level $\le$ your level); swap 1 card; +1 skill point (caps: 5, then 7 at L5+, 10 at L9+) \\
\textbf{Even levels} & +1 Deed rank (new deed at I, or upgrade one held) \\
\textbf{L3 / L6 / L9} & +1 Alignment point (cap 5, then 7 at L9+) \\
\textbf{L4 / L8} & +1 Moderate threshold \textit{and} +1 Major threshold \\
\textbf{L5 / L7 / L9} & +1 to one of Strike, Shoot (improve target by 1, min 2+) or Defend (max 3) --- a different stat each time \\
\end{tabular}
\end{center}

GM awards (deed ranks for deeds done, cards for techniques earned in fiction) ride on top of the ladder, never instead of it.

\medskip\hrule\medskip

\section{Wounds, Healing, and Old Cards (Conversion Sidebar)}

The wound system replaced hit points; two conversions keep every earlier document current until their next revision:

\textbf{Healing.} Where a card says \textit{heal N HP}: each 2 points of that healing \textbf{clears one minor wound}; each 3 points \textbf{reduces one wound a severity step} (major$\to$moderate$\to$minor$\to$closed). \textit{Stabilize} effects halt Bleeding/Dying as written. Effects that said \textit{"drops to 1 HP instead of 0"} now read \textit{"you are not Dying/downed by this wound; it lands one severity lower."}

\textbf{Deathproof (deed) reads as:} \textbf{I} +1 Moderate threshold; \textbf{II} +1 Major threshold and +1 die on saves while carrying a major wound; \textbf{III} unchanged in spirit --- once per scene, when a wound would leave you Dying, it leaves you disabled instead; \textbf{IV} unchanged --- once per session, a Death result is Dying instead. \textit{("Too mean to bury" survives translation intact.)}

\medskip\hrule\medskip

\section{Design Notes: Where the Numbers Sit}

The thresholds and the Equipment chapter's weapon values were set together and tested against the wound tables' lethality (majors kill 41.7\% before saves). The tuning targets, verified by simulation: an \textbf{unarmored average character} (Mod 4/Maj 8, Defend 0) facing a revolver is at even odds of dying inside three volleys and near-certain inside five --- the open street is death, and the game means it; a \textbf{hardened, armored veteran} (Mod 5/Maj 10, Defend 1, leathers) weathers ten; a \textbf{knife} almost never kills a healthy target quickly but rides the wound spiral viciously as a finisher; and \textbf{heavy plate defeats even a buffalo gun} until armor-piercing rounds come out, which is what they are for. Cover, Defend, armor, and going first are worth more than any weapon upgrade --- exactly the economy a gunfight should have.
